### 2022-06-30 manuscript/Template for submissions to Scientific Reports/main.tex
Changed the multiplication factor of the direction-selective resistance from 50 to 20.

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\title{Direction-selective Resistance to Cerebrospinal Fluid Flow as The
Mechanism of Syrinx Generation in Syringomyelia}

\author{Han Soo Chang, M.D.}
\affil{Department of Neurosurgery, Tokai University\\Isehara, Japan}

\keywords{syringomyelia, pathophysiology, simulation}

\begin{abstract}
Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations.
\end{abstract}
\begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The pathophysiology of syringomyelia is still poorly understood. A number
of hypotheses exist in the literature [@gardner1958mechanism;
@williams1980pathogenesis; @milhorat1999chiari; @ball1972pathogenesis;
@klekamp2002pathophysiology; @duboulay1974mechanism; @heiss1999elucidating;
@milhorat1993anatomical; @stoodley2000pathophysiology; @terae1994increased;
@chang2003hypothesis; @chang2004theoretical; @greitz2006unraveling], but
they provide widely different explanations on the mechanisms of syrinx
generation.  Most researchers, nevertheless, seem to agree on the following
points. First, the syrinx fluid is identical to the CSF, and there should
be some communication between the syrinx and the subarachnoid space. This
point is supported by many studies [@ellertsson1969syringomyelia;
@ellertsson1969myelocystographic; @li1987conventional; @heiss2019origin],
although a few different opinions exist [@greitz2006unraveling;
@koyanagi1997surgical]. Second, some derangement of CSF flow in the spinal
subarachnoid space causes syrinx both in Chiari-I malformation
[@wolpert1994chiari; @bhadelia1995cerebrospinal; @heiss1999elucidating;
@hofmann2000phasecontrast; @quigley2004cerebrospinal] and subarachnoid
arachnopathy [@klekamp1997treatment; @brodbelt2003altered;
@heiss2012pathophysiology; @chang2014dorsal]. The cerebellar tonsils hamper
the CSF flow in the former and adhesive arachnoiditis in the latter.

The problem, however, is where this communicating channel resides and what
mechanism generates the syrinx. On these points, there is no solid
experimental or clinical evidence, and the opinions of researchers deviate
widely. Gardner et al. [@gardner1958mechanism] thought that the central
canal intercommunicates the syrinx and the fourth ventricle, and arterial
pressure waves exerted on the central canal generate the syrinx. Williams
et al. also postulated the communication through the central canal, but for
the syrinx generation mechanism, he emphasized the craniospinal pressure
gradient produced by Valsalva maneuver et al.  On the other hand, Ball and
Dayan [@ball1972pathogenesis] assumed that CSF enters the syrinx through
the perivascular space of arteries penetrating the spinal cord. This idea
has the following variations. Heiss et al. [@heiss1999elucidating] proposed
that the piston-like movement of the cerebellar tonsils in Chiari-I
patients generates pressure waves in the spinal subarachnoid space, which
subsequently drive CSF into the syrinx through the perivascular space.
Stoodley et al. also considered the perivascular space as the communicating
channel, but he assumed the arterial pulse pressure as the driving force of
CSF [@stoodley2000mechanisms]

All these assumptions are not proven and remain hypothetical. Although the
perivascular-space theory seems to be favored by recent researchers, there
remains the possibility that a thin communicating channel exists between
the syrinx and the fourth ventricle [@chang2021hypothesis].  In our
opinion, the main theoretical problems reside in the following points.
\begin{enumerate}
    \item No theory can explain the pathophysiological mechanism of syringomyelia in a unified fashion.
    \item No theory can explain how CSF enters from the low-pressure subarachnoid space to the high-pressure syrinx cavity and remains inside.
\end{enumerate}

As to the first point, there are different syringomyelia types, such as
Chiari-I-malformation and spinal-arachnopathy-related. The
Chiari-I-malformation-related syringomyelia is further divided into
communicating and non-communicating. For each of them, current theories
assume a distinct mechanism of syrinx generation. However, it may be more
natural to conjecture some common mechanism underlying these different
types of syringomyelia [@stoodley2000mechanisms].  The second point is
theoretically essential but challenging to solve. Physical theories dictate
that the expanded syrinx cavity has higher pressure than the subarachnoid
space [@serwayr.a.2016fluids; @heiss1999elucidating; @davis1989mechanisms;
@ellertsson1970distending]. Therefore, merely assuming a communicating
channel does not explain how CSF enters the syrinx and remains inside
against this pressure gradient. Even if we take a specific time window
where the subarachnoid pressure exceeds the syrinx pressure, it does not
explain how the CSF remains inside the syrinx after it.

The current article is part of our effort to solve the above theoretical
problems. In our previous paper [@chang2021hypothesis], we hypothesized
that if there is a resistance to CSF flow in a particular direction
(rostral or caudal), it causes a one-way valve-like effect on a CSF channel
inside the spinal cord, leading to the accumulation of CSF and generation
of a syrinx. This hypothesis could explain the pathophysiology of both
Chiari-I-malformation-related syringomyelia and arachnopathy-related
syringomyelia. In Chiari-I-malformation-related syringomyelia, the
herniated cerebellar tonsils may function as a direction-selective
resistance. In arachnopathy-related syringomyelia, some arachnoid adhesion
may play the same function.  However, in that article, we just drew a rough
sketch of this process and left out a detailed explanation. The current
article will describe in detail how direction-selective resistance in the
subarachnoid space generates a one-way valve mechanism in the CSF channel
inside the spinal cord.

For this purpose, we used a mathematical model simulating the CSF movement
of the spine—a revised version of our previous model [@chang2003hypothesis;
@chang2004theoretical]. This model describes the spinal CSF movement as an
electric current in a modeled circuit (a lumped parameter model with
multiple compartments [@shi2011review]), and it assumes the existence of a
patent central canal. We placed a direction-selective resistance in this
model at a certain point in the spinal subarachnoid space and observed how
it affects the CSF flow in the central canal.  \section*{Results}

\section*{Discussion}

The Discussion should be succinct and must not contain subheadings.

\section*{Methods}

Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.

\bibliography{sample}

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Hao:gidmaps:2014}.

For data citations of datasets uploaded to e.g. \emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.

\section*{Acknowledgements (not compulsory)}

Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

\section*{Author contributions statement}

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.

\section*{Additional information}

To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement).

The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{stream}
\caption{Legend (350 words max). Example legend text.}
\label{fig:stream}
\end{figure}

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
Condition & n & p \\
\hline
A & 5 & 0.1 \\
\hline
B & 10 & 0.01 \\
\hline
\end{tabular}
\caption{\label{tab:example}Legend (350 words max). Example legend text.}
\end{table}

Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

\end{document}

### 2022-06-30 manuscript/draft.tex
Changed the multiplication factor of the direction-selective resistance from 50 to 20.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[a4paper,12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{newtxtext}
\title{On the Pathophysiology of Syringomyelia}
\author{Han Soo Chang, M.D.}
\date{}

\begin{document}
\maketitle
\subsection{Introduction}

The pathophysiology of syringomyelia is still poorly understood. There is a substantial variety of hypotheses in the literature\textsuperscript{1--13}, and their explanations on the mechanisms of syrinx generation differ widely. We may, however, identify some points of consensus among many researchers.

Syrinx generation is related to some derangement in CSF flow in the spinal subarachnoid space.

Syrinx generation is related to some derangement in CSF flow in the spinal subarachnoid space.

Several studies support the first point\textsuperscript{14--17}, although not without disagreement\textsuperscript{13,18}. Numerous studies support the second point in the case of Chiari I malformation, where the herniated tonsils partially obstruct the subarachnoid CSF movement\textsuperscript{7,19--22}. Altered subarachnoid CSF movement also plays an essential role in syringomyelia associated with arachnopathy\textsuperscript{23--26}.

The problem, however, is where this communicating channel is and what mechanism generates the syrinx. On these points, there is no solid experimental or clinical evidence, and the opinions of researchers deviate widely. Gardner et al.\textsuperscript{1} thought that the central canal communicates the syrinx and the fourth ventricle, and arterial pressure waves exerted on the central canal generate the syrinx. Williams et al.~also postulated the communication through the central canal, but for the syrinx generation mechanism, he emphasized the craniospinal pressure gradient produced by Valsalva maneuver et al.

On the other hand, Ball and Dayan\textsuperscript{4} assumed that CSF enters the syrinx through the perivascular space of arteries penetrating the spinal cord. This idea is also supported by recent researchers. Heiss et al\textsuperscript{7} proposed that the piston-like movement of the cerebellar tonsils in Chiari-I patients generate pressure waves in the spinal subarachnoid space, which subsequently drive CSF into the syrinx through the perivascular space. Stoodley et al.~also considered the perivascular space as the communicating channel, but he assumed the arterial pulse pressure as the driving force of CSF\textsuperscript{\textbf{stoodley2000mechanisms?}}

All these assumptions are not proven and remain hypothetical. Although the perivascular space theory seems to be favored by recent researchers, there still remains the possibility that a thin communicating channel exists between the syrinx and the fourth ventricle\textsuperscript{\textbf{chang2021hypothesis?}}.

In our opinion, the main theoretical problems reside in the following points.

No theory can explain how CSF enters from the low-pressure subarachnoid space to the high-pressure syrinx cavity and remains inside.

No theory can explain the pathophysiological mechanism of syringomyelia in a unified fashion.

As to the first point, there are different types of syringomyelia, such as Chiari-I-malformation-related and spinal-arachnopathy-related. The Chiari-I-malformation-related syringomyelia is further divided into communicating and non-communicating. For each of them, current theories appear to assume a distinct mechanism of syrinx generation. However, it may be more natural to conjecture some common mechanism underlying these different types of syringomyelia\textsuperscript{\textbf{stoodley2000mechanisms?}}.

The second point is theoretically important but difficult to solve. Clearly, the syrinx cavity must have higher pressure than the subarachnoid space\textsuperscript{7,27--29}. Therefore, merely assuming a communicating channel is insufficient to explain how CSF enters the syrinx and remains inside against this pressure gradient. Even if we assume that there is a certain time window where the subarachnoid pressure exceeds the syrinx pressure, it does not explain how the CSF is retained inside the syrinx after that time window is passed.

The current article is part of our attempt to solve the above theoretical problems. In our previous paper\textsuperscript{\textbf{chang2021hypothesis?}}, we proposed a hypothesis that if there is a direction-selective resistance in the spinal subarachnoid space, it causes a one-way valve like effect on a CSF channel inside the spinal cord, leading to accumulation of CSF and generation of a syrinx. This hypothesis was attractive because the herniated tonsil in Chiari-I malformation could be easily conceived as a direction-selective resistance, and it could provide a common mechanism underlying different types of syringomyelia.

In that article, however, we just drew a rough sketch of this process and left out a detailed explanation. In the current article, we will describe in detail how a direction-selective resistance in the subarachnoid space generates a one-way valve mechanism in the CSF channel inside the spinal cord.

For this purpose, we used a mathematical model simulating the CSF movement of the spine---a revised version of our previous model\textsuperscript{11,12}. This model of the spinal CSF movement was a lumped parameter model with multiple compartments\textsuperscript{30} and it assumed the existence of a patent central canal. We placed a direction-selective resistance in a certain point in the spinal subarachnoid space in this model, and observed how it affects the CSF flow in the central canal.

Material and Method

We can analyze the motion of biological fluids such as blood and CSF using computer simulation. However, the biological fluids flow inside elastic conduits and require different analysis techniques from those used in the engineering field, where the boundary of the conduit is supposed to be solid. For this purpose, researchers widely used the lumped parameter model\textsuperscript{30,31}. This model considers the fluid flow inside an elastic conduit in analogy to the electric flow in an electric circuit. The accumulation of electricity in a capacitor represents the expansion of the elastic arterial wall and the accompanying pressure elevation. An electrical resistor represents the frictional resistance to flow. This model has a wide variety. For example, it may model the whole cardiovascular system as one electric circuit, or it may model it as a synthesis of multiple compartments of an electric circuit\textsuperscript{30,31}.

The purpose of the current study was not to make a quantitatively precise model of the spinal CSF flow but to make a basic model that reveals the phenomenon underlying the generation of syringomyelia. For this purpose, we adopted a revised version of our previous lumped parameter model with multiple compartments.

Previously, we developed a mathematical model that simulated the CSF flow in the spine\textsuperscript{11};\textsuperscript{12}{]}. This model was a multiple-compartment version of a 1-dimensional lumped parameter model, and could describe the CSF movement in the whole spine. Figure 1 shows the scheme of this model representing the CSF system of the spine as an electric circuit. The whole circuit could be described by a system of differential equations, and its behavior to a cranial pressure wave (described as a boundary condition on the cranial points) could be numerically calculated using a computer software.

This time, we improved the previous model as follows.

We increased the number of compartments from 10 to 100, thereby making the model more precise.

We estimated the values of the parameters (the capacitance and resistance of each component) of the model as follows so that the model will become more realistic.

First, we set the length of the modeled spinal cord to be 1 meter.

The resistance of the subarachnoid space (R) was estimated using the following equations of Poisseuille\textsuperscript{32--34}.

\[\Delta P=\frac{8\pi \mu{}LQ}{A^{2}}=RQ\]

\[\Delta P\]: Pressure difference between the adjacent compartments

Q: flow speed per unit surface

\[\mu\]: viscosity coefficient. In this case, it was set to the value of water (0.0007).

L: distance between the adjacent compartments. It was set to 1 cm.

A: cross sectional area of the subarachnoid space. It was set to the value of a concentric annulus\textsuperscript{34} with the outer diameter of 1cm and the inner diameter of 0.7 cm (\[1.6\times{}10^{-4} (m^2)\])

Thus, \textbf{R} was calculated to be \[6872\hspace{0.2cm}(Pa\cdot{}sec/m^3)\]

The resistance of the central canal (r) was estimated using the same equation with \[A\] set to \[\pi{}(10^{-4})^2\hspace{0.1cm}(m^2)\], i.e.~the cross sectional area of a tube with a diameter of 100 \[\mu{}m\]. Thus, \textbf{r} was calculated to be \[1.78\times10^{11}\hspace{0.2cm}(Pa\cdot{}sec/m^3)\]

We determined the capacitance (\[C_{sub}\])corresponding to the dural elasticity so that the pressure-wave velocity determined by the time constant (\[RC\]) will roughly correspond to the pressure-wave velocity of the downward CSF wave observed in phase-contrast MRI of normal individuals. Thus, we set \[C_{sub}=0.1\hspace{0.2cm}(m^3/Pa\cdot{}sec)\].

The scheme of the constructed electric circuit model is shown in Figure 1. This model represents the CSF movement in the spine as electric flow along multiple compartments of capacitances connected with resistors. The values of the resistors and capacitors are shown in Table 1.

The behavior of this electric circuit is described by a set of differential equations with the voltage at the cranial nodes as the boundary condition. In the previous articles\textsuperscript{11,12}, we only analyzed the transient behavior of the model to a sudden pressure increase on the cranial side of the subarachnoid space. This analysis was useful in simulating the situation of coughing or Valsalva maneuvers. In this article, however, we analyzed the steady-state response of the model to an oscillating cranial pressure wave simulating the normal cardiac pulsation of the CSF.

We numerically solved the differential equations using a computer software (Mathematica version 12, Wolfram Research, Champaign, IL, U.S.A.). The boundary conditions were set as follows. (1) The voltage at the two cranial nodes was set to a sine wave oscillating around 100 mmHg with an amplitude of 20 mmHg at one cycle per second. (2) The initial dural pressure was set at 100 mmHg in all segments. The step of the numerical solution was set to 1/5000 second, and the solution was calculated from zero to 20 seconds. The obtained solution was displayed as a movie and was exported to a file in the mp4 format.

Results

This section presents the system's responses as videos. Each video displays either all or some of the following four values simultaneously: namely, the dural tension (voltage in D capacitors in Figure 2), the canal tension (voltages in C capacitors), the subarachnoid CSF flow (flows in R resistors), and the canal flow (flows in r resistors). We plotted the node position on the x-axis and the values at that node on the y-axis. The pressure values are shown in \[cmH_2O\], the flows in \[ml/sec\]. To plot different ranges of values in a single plot, we multiplied the following values with certain coefficients: namely, the canal tension with 50, the subarachnoid flow with 0.005, and the canal flow with \[1.5\times10^{5}\]. We plotted the rightward flow in the positive and the leftward flow in the negative direction.

Video 1 shows the original system's response to the sine wave input on the cranial side. In this condition, CSF makes a smooth to-and-fro movement in the subarachnoid space with the corresponding pressure wave along the dura and the central canal. This response corresponds to the CSF dynamics in a normal individual.

In Video 2, we increased the subarachnoid resistance \[R_{25}\] by 20 times, thereby simulating a simple block of the subarachnoid flow in both directions. In this condition, the dural tension showed a pressure drop at node 25, corresponding to the increased resistance both in caudal and rostral flow phases. This pressure drop caused an increase in canal flow in a direction identical to the subarachnoid CSF flow. This increased canal flow caused a transient increase in canal pressure distal to the block and a decrease proximal to the block. However, these pressure changes alternated according to the flow phase and did not produce a sustained condition.

In Video 3, we replaced the subarachnoid resistor \[R_{25}\] with a one-way valve that selectively resisted flow in the caudal direction by 50 times. This time, the dural tension curve showed a pressure drop across node 25, appearing only during the caudal-flow phase. Canal flow showed alternating increase in caudal and rostral directions according to the flow phase, which was similar to that in the simple block above. However, there was a significant difference. Sustained high pressure appeared in the central canal distal to the valve, and some sustained low pressure in the segment proximal to the valve. The canal flow near node 25 markedly increased caudally in the caudal-flow phase and rostrally in the rostral-flow phase. We took out the canal flow and showed it in Video 4. Observing this video, we can see that the cumulative total of the caudal flow is larger than that of the rostral flow, and it means that the CSF is virtually pumped caudally at node 25.

Discussion

In this article, we theoretically analyzed the CSF movement in the spinal cord using a lumped parameter model with multiple components. It simulated a system with an elastic tube (dura) containing an elastic cylindrical material (spinal cord) that itself contained a fluid channel (the central canal). When we placed a direction-selective resistor in the subarachnoid channel and evoked a to-and-fro pressure wave on this system, it produced a sustained pressure elevation in the segment distal to the direction-selective resistor. This phenomenon may explain the pathogenesis of syringomyelia both in Chiari I malformation and syringomyelia associated with arachnopathy.

Subarachnoid pressure affects the pressure inside the central canal. As seen in Figure 2, the absolute pressure inside the central canal is the sum of the subarachnoid and canal pressure (voltages of \[C_k\] and \[D_k\] in electrical terms). Suppose a one-way valve selectively resists caudal flow in the subarachnoid space at point A, and CSF makes a to-and-fro movement across it. The caudal-flow phase creates a pressure drop across point A, making the subarachnoid pressure in the distal segment smaller, and it reduces the absolute canal pressure in the distal segment. Thus, the pressure gradient in the central canal across point A increases, which increases the distal CSF flow in the canal at that point.

On the contrary, the rostral flow does not create a pressure drop. Although some of the CSF pumped caudally will flow back rostrally, its amount will be smaller. The net result will be that some CSF is pumped caudally in one cycle of the to-and-fro movement. Thus, CSF gradually accumulates in the distal segment of the resistance. We hypothesize that this is the mechanism underlying the syrinx generation.

This hypothesis solves the theoretical problems pointed out in the Introduction. A one-way valve in subarachnoid space creates an asymmetry of the pressure gradient between the caudal and rostral flow phases in the central canal. This asymmetric alternation of pressure gradient effectively pumps CSF caudally, creating sustained pressure elevation in the caudal segment. In other words, the energy of the to-and-fro CSF movement is translated via the one-way valve into the creation and sustenance of syringomyelia.

Direction-selective resistance to CSF flow is not an imaginative assumption but actually exists in patients. In Chiari-I malformation, the herniated tonsils move like a ball-valve, displaced caudally during the caudal flow and rostrally during the rostral flow. Higher velocity observed in the phase-contrast MRI studies suggests that it selectively impedes the caudal CSF flow more than the cranial flow. This direction-selective resistance was demonstrated by Williams in direct measurements in Chiari-I patients and became the basis of his theory\textsuperscript{\textbf{williams1981simultaneous?}}.

Also, there is a possibility that some types of arachnoid pathology function as one-way valves. In 2014, we reported a case of thoracic arachnoid web associated with syringomyelia, in which phase-contrast MRI detected one-way-valve-like behavior of the arachnoid web\textsuperscript{26}. We found an obliquely oriented arachnoid web that reminded us of a one-way valve in surgery. Thus, our hypothesis may also solve the second theoretical problem that we pointed out in the Introduction. Namely, we may consider the presence of a one-way valve in spinal subarachnoid space as a common mechanism underlying both Chiari-I-related and arachnopathy-related syringomyelia.

Our theory assumes that the arterial-pulse generated to-and-fro CSF movement provides the energy for syrinx generation. It is compatible with Stoodley et al.'s experimental result that syrinx maintenance is dependent on arterial pulsation\textsuperscript{\textbf{stoodley2000mechanisms?}}. In this study, the authors showed that

Conclusions

References

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-gardner1958mechanism}{}}%
\CSLLeftMargin{1. }
\CSLRightInline{Gardner WJ, Angel J. The mechanism of syringomyelia and its surgical correction. \emph{Clin Neurosurgery}. 1958;6:131-140.}

\leavevmode\vadjust pre{\hypertarget{ref-williams1980pathogenesis}{}}%
\CSLLeftMargin{2. }
\CSLRightInline{Williams B. \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1437943}{On the pathogenesis of syringomyelia: A review}. \emph{Journal of the Royal Society of Medicine}. 1980;73(11):798-806.}

\leavevmode\vadjust pre{\hypertarget{ref-milhorat1999chiari}{}}%
\CSLLeftMargin{3. }
\CSLRightInline{Milhorat TH, Chou MW, Trinidad EM, et al. Chiari {I} malformation redefined: Clinical and radiographic findings for 364 symptomatic patients. \emph{Neurosurgery}. 1999;44(5):1005-1017. doi:\href{https://doi.org/10.1097/00006123-199905000-00042}{10.1097/00006123-199905000-00042}}

\leavevmode\vadjust pre{\hypertarget{ref-ball1972pathogenesis}{}}%
\CSLLeftMargin{4. }
\CSLRightInline{Ball MJ, Dayan AD. Pathogenesis of syringomyelia. \emph{Lancet (London, England)}. 1972;2(7781):799-801. doi:\href{https://doi.org/10.1016/s0140-6736(72)92152-6}{10.1016/s0140-6736(72)92152-6}}

\leavevmode\vadjust pre{\hypertarget{ref-klekamp2002pathophysiology}{}}%
\CSLLeftMargin{5. }
\CSLRightInline{Klekamp J. The pathophysiology of syringomyelia - historical overview and current concept. \emph{Acta Neurochirurgica}. 2002;144(7):649-664. doi:\href{https://doi.org/10.1007/s00701-002-0944-3}{10.1007/s00701-002-0944-3}}

\leavevmode\vadjust pre{\hypertarget{ref-duboulay1974mechanism}{}}%
\CSLLeftMargin{6. }
\CSLRightInline{Boulay G du, Shah SH, Currie JC, Logue V. The mechanism of hydromyelia in {Chiari} type 1 malformations. \emph{The British Journal of Radiology}. 1974;47(561):579-587. doi:\href{https://doi.org/10.1259/0007-1285-47-561-579}{10.1259/0007-1285-47-561-579}}

\leavevmode\vadjust pre{\hypertarget{ref-heiss1999elucidating}{}}%
\CSLLeftMargin{7. }
\CSLRightInline{Heiss JD, Patronas N, DeVroom HL, et al. Elucidating the pathophysiology of syringomyelia. \emph{Journal of Neurosurgery}. 1999;91(4):553-562. doi:\href{https://doi.org/10.3171/jns.1999.91.4.0553}{10.3171/jns.1999.91.4.0553}}

\leavevmode\vadjust pre{\hypertarget{ref-milhorat1993anatomical}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{Milhorat TH, Miller JI, Johnson WD, Adler DE, Heger IM. Anatomical basis of syringomyelia occurring with hindbrain lesions. \emph{Neurosurgery}. 1993;32(5):748-754; discussion 754. doi:\href{https://doi.org/10.1227/00006123-199305000-00008}{10.1227/00006123-199305000-00008}}

\leavevmode\vadjust pre{\hypertarget{ref-stoodley2000pathophysiology}{}}%
\CSLLeftMargin{9. }
\CSLRightInline{Stoodley MA. \href{https://www.ncbi.nlm.nih.gov/pubmed/10839277}{Pathophysiology of syringomyelia}. \emph{Journal of Neurosurgery}. 2000;92(6):1069-1070; author reply 1071-1073.}

\leavevmode\vadjust pre{\hypertarget{ref-terae1994increased}{}}%
\CSLLeftMargin{10. }
\CSLRightInline{Terae S, Miyasaka K, Abe S, Abe H, Tashiro K. \href{https://www.ncbi.nlm.nih.gov/pubmed/8183451}{Increased pulsatile movement of the hindbrain in syringomyelia associated with the {Chiari} malformation: Cine-{MRI} with presaturation bolus tracking}. \emph{Neuroradiology}. 1994;36(2):125-129.}

\leavevmode\vadjust pre{\hypertarget{ref-chang2003hypothesis}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{Chang HS, Nakagawa H. \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1738338}{Hypothesis on the pathophysiology of syringomyelia based on simulation of cerebrospinal fluid dynamics}. \emph{Journal of Neurology, Neurosurgery, and Psychiatry}. 2003;74(3):344-347.}

\leavevmode\vadjust pre{\hypertarget{ref-chang2004theoretical}{}}%
\CSLLeftMargin{12. }
\CSLRightInline{Chang HS, Nakagawa H. \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1763562}{Theoretical analysis of the pathophysiology of syringomyelia associated with adhesive arachnoiditis}. \emph{Journal of Neurology, Neurosurgery, and Psychiatry}. 2004;75(5):754-757.}

\leavevmode\vadjust pre{\hypertarget{ref-greitz2006unraveling}{}}%
\CSLLeftMargin{13. }
\CSLRightInline{Greitz D. Unraveling the riddle of syringomyelia. \emph{Neurosurgical Review}. 2006;29(4):251-263; discussion 264. doi:\href{https://doi.org/10.1007/s10143-006-0029-5}{10.1007/s10143-006-0029-5}}

\leavevmode\vadjust pre{\hypertarget{ref-ellertsson1969syringomyelia}{}}%
\CSLLeftMargin{14. }
\CSLRightInline{Ellertsson AB. Syringomyelia and other cystic spinal cord lesions. \emph{Acta Neurologica Scandinavica}. 1969;45(4):403-417. doi:\href{https://doi.org/10.1111/j.1600-0404.1969.tb01254.x}{10.1111/j.1600-0404.1969.tb01254.x}}

\leavevmode\vadjust pre{\hypertarget{ref-ellertsson1969myelocystographic}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{Ellertsson AB, Greitz T. \href{https://www.ncbi.nlm.nih.gov/pubmed/5820121}{Myelocystographic and fluorescein studies to demonstrate communication between intramedullary cysts and the cerebrospinal fluid space}. \emph{Acta Neurologica Scandinavica}. 1969;45(4):418-430.}

\leavevmode\vadjust pre{\hypertarget{ref-li1987conventional}{}}%
\CSLLeftMargin{16. }
\CSLRightInline{Li KC, Chui MC. \href{https://www.ncbi.nlm.nih.gov/pubmed/3101451}{Conventional and {CT} metrizamide myelography in {Arnold}-{Chiari} {I} malformation and syringomyelia}. \emph{AJNR American journal of neuroradiology}. 1987;8(1):11-17.}

\leavevmode\vadjust pre{\hypertarget{ref-heiss2019origin}{}}%
\CSLLeftMargin{17. }
\CSLRightInline{Heiss JD, Jarvis K, Smith RK, et al. Origin of {Syrinx} {Fluid} in {Syringomyelia}: {A} {Physiological} {Study}. \emph{Neurosurgery}. 2019;84(2):457-468. doi:\href{https://doi.org/10.1093/neuros/nyy072}{10.1093/neuros/nyy072}}

\leavevmode\vadjust pre{\hypertarget{ref-koyanagi1997surgical}{}}%
\CSLLeftMargin{18. }
\CSLRightInline{Koyanagi I, Iwasaki Y, Hida K, Abe H, Isu T, Akino M. Surgical treatment supposed natural history of the tethered cord with occult spinal dysraphism. \emph{Child's Nervous System: ChNS: Official Journal of the International Society for Pediatric Neurosurgery}. 1997;13(5):268-274. doi:\href{https://doi.org/10.1007/s003810050081}{10.1007/s003810050081}}

\leavevmode\vadjust pre{\hypertarget{ref-wolpert1994chiari}{}}%
\CSLLeftMargin{19. }
\CSLRightInline{Wolpert SM, Bhadelia RA, Bogdan AR, Cohen AR. \href{https://www.ncbi.nlm.nih.gov/pubmed/7976942}{Chiari {I} malformations: Assessment with phase-contrast velocity {MR}}. \emph{AJNR American journal of neuroradiology}. 1994;15(7):1299-1308.}

\leavevmode\vadjust pre{\hypertarget{ref-bhadelia1995cerebrospinal}{}}%
\CSLLeftMargin{20. }
\CSLRightInline{Bhadelia RA, Bogdan AR, Wolpert SM, Lev S, Appignani BA, Heilman CB. Cerebrospinal fluid flow waveforms: Analysis in patients with {Chiari} {I} malformation by means of gated phase-contrast {MR} imaging velocity measurements. \emph{Radiology}. 1995;196(1):195-202. doi:\href{https://doi.org/10.1148/radiology.196.1.7784567}{10.1148/radiology.196.1.7784567}}

\leavevmode\vadjust pre{\hypertarget{ref-hofmann2000phasecontrast}{}}%
\CSLLeftMargin{21. }
\CSLRightInline{Hofmann E, Warmuth-Metz M, Bendszus M, Solymosi L. \href{https://www.ncbi.nlm.nih.gov/pubmed/10669242}{Phase-contrast {MR} imaging of the cervical {CSF} and spinal cord: Volumetric motion analysis in patients with {Chiari} {I} malformation}. \emph{AJNR American journal of neuroradiology}. 2000;21(1):151-158.}

\leavevmode\vadjust pre{\hypertarget{ref-quigley2004cerebrospinal}{}}%
\CSLLeftMargin{22. }
\CSLRightInline{Quigley MF, Iskandar B, Quigley ME, Nicosia M, Haughton V. Cerebrospinal fluid flow in foramen magnum: Temporal and spatial patterns at {MR} imaging in volunteers and in patients with {Chiari} {I} malformation. \emph{Radiology}. 2004;232(1):229-236. doi:\href{https://doi.org/10.1148/radiol.2321030666}{10.1148/radiol.2321030666}}

\leavevmode\vadjust pre{\hypertarget{ref-klekamp1997treatment}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{Klekamp J, Batzdorf U, Samii M, Bothe HW. Treatment of syringomyelia associated with arachnoid scarring caused by arachnoiditis or trauma. \emph{Journal of Neurosurgery}. 1997;86(2):233-240. doi:\href{https://doi.org/10.3171/jns.1997.86.2.0233}{10.3171/jns.1997.86.2.0233}}

\leavevmode\vadjust pre{\hypertarget{ref-brodbelt2003altered}{}}%
\CSLLeftMargin{24. }
\CSLRightInline{Brodbelt AR, Stoodley MA, Watling AM, Tu J, Burke S, Jones NR. Altered subarachnoid space compliance and fluid flow in an animal model of posttraumatic syringomyelia. \emph{Spine}. 2003;28(20):E413-419. doi:\href{https://doi.org/10.1097/01.BRS.0000092346.83686.B9}{10.1097/01.BRS.0000092346.83686.B9}}

\leavevmode\vadjust pre{\hypertarget{ref-heiss2012pathophysiology}{}}%
\CSLLeftMargin{25. }
\CSLRightInline{Heiss JD, Snyder K, Peterson MM, et al. Pathophysiology of primary spinal syringomyelia. \emph{Journal of Neurosurgery Spine}. 2012;17(5):367-380. doi:\href{https://doi.org/10.3171/2012.8.SPINE111059}{10.3171/2012.8.SPINE111059}}

\leavevmode\vadjust pre{\hypertarget{ref-chang2014dorsal}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{Chang HS, Nagai A, Oya S, Matsui T. Dorsal spinal arachnoid web diagnosed with the quantitative measurement of cerebrospinal fluid flow on magnetic resonance imaging. \emph{Journal of Neurosurgery Spine}. 2014;20(2):227-233. doi:\href{https://doi.org/10.3171/2013.10.SPINE13395}{10.3171/2013.10.SPINE13395}}

\leavevmode\vadjust pre{\hypertarget{ref-serwayr.a.2016fluids}{}}%
\CSLLeftMargin{27. }
\CSLRightInline{Serway, R. A. Fluids and {Solids}. In: \emph{College Physics}. 11th ed. Cengage Learning; 2016:267-319.}

\leavevmode\vadjust pre{\hypertarget{ref-davis1989mechanisms}{}}%
\CSLLeftMargin{28. }
\CSLRightInline{Davis CH, Symon L. Mechanisms and treatment in post-traumatic syringomyelia. \emph{British Journal of Neurosurgery}. 1989;3(6):669-674. doi:\href{https://doi.org/10.3109/02688698908992690}{10.3109/02688698908992690}}

\leavevmode\vadjust pre{\hypertarget{ref-ellertsson1970distending}{}}%
\CSLLeftMargin{29. }
\CSLRightInline{Ellertsson AB, Greitz T. The distending force in the production of communicating syringomyelia. \emph{Lancet (London, England)}. 1970;1(7658):1234. doi:\href{https://doi.org/10.1016/s0140-6736(70)91829-5}{10.1016/s0140-6736(70)91829-5}}

\leavevmode\vadjust pre{\hypertarget{ref-shi2011review}{}}%
\CSLLeftMargin{30. }
\CSLRightInline{Shi Y, Lawford P, Hose R. Review of {Zero}-{D} and 1-{D} {Models} of {Blood} {Flow} in the {Cardiovascular} {System}. \emph{BioMedical Engineering OnLine}. 2011;10(1):33. doi:\href{https://doi.org/10.1186/1475-925X-10-33}{10.1186/1475-925X-10-33}}

\leavevmode\vadjust pre{\hypertarget{ref-kokalari2013review}{}}%
\CSLLeftMargin{31. }
\CSLRightInline{Kokalari I, Karaja T, Guerrisi M. Review on lumped parameter method for modeling the blood flow in systemic arteries. \emph{J Biomed Sci Eng}. 2013;6(1):92-99.}

\leavevmode\vadjust pre{\hypertarget{ref-brook1999numerical}{}}%
\CSLLeftMargin{32. }
\CSLRightInline{Brook BS, Falle S, Pedley TJ. Numerical solutions for unsteady gravity-driven flows in collapsible tubes: Evolution and roll-wave instability of a steady state. \emph{Journal of Fluid Mechanics}. 1999;396:223-256.}

\leavevmode\vadjust pre{\hypertarget{ref-sherwin2003computational}{}}%
\CSLLeftMargin{33. }
\CSLRightInline{Sherwin SJ, Formaggia L, Peiro J, Franke V. Computational modelling of {1D} blood flow with variable mechanical properties and its application to the simulation of wave propagation in the human arterial system. \emph{International journal for numerical methods in fluids}. 2003;43(6-7):673-700.}

\leavevmode\vadjust pre{\hypertarget{ref-huilgol2020fast}{}}%
\CSLLeftMargin{34. }
\CSLRightInline{Huilgol RR, Georgiou GC. A fast numerical scheme for the {Poiseuille} flow in a concentric annulus. \emph{Journal of Non-Newtonian Fluid Mechanics}. 2020;285:104401. doi:\href{https://doi.org/10.1016/j.jnnfm.2020.104401}{10.1016/j.jnnfm.2020.104401}}

\end{CSLReferences}

\backmatter
\end{document}

### 2022-06-30 manuscript/main.tex
Changed the multiplication factor of the direction-selective resistance from 50 to 20.

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\title{Direction-Selective Resistance to Cerebrospinal-Fluid Flow As
the Mechanism of Syrinx Generation in Syringomyelia}

\author{Han Soo Chang, M.D.}
\affil{Department of Neurosurgery, Tokai University\\Isehara, Japan}

\keywords{syringomyelia, pathophysiology, simulation}

\begin{abstract}
    The pathophysiology of syringomyelia is not well understood. The main
    theoretical problem is how cerebrospinal fluid (CSF) enters from
    low-pressure subarachnoid space to high-pressure syrinx and stays
    there.
\end{abstract} \begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The pathophysiology of syringomyelia is still poorly understood. A number
of hypotheses exist in the literature \cite{gardner1958mechanism,
williams1980pathogenesis, milhorat1999chiari, ball1972pathogenesis,
klekamp2002pathophysiology, duboulay1974mechanism, heiss1999elucidating,
milhorat1993anatomical, stoodley2000pathophysiology, terae1994increased,
chang2003hypothesis, chang2004theoretical, greitz2006unraveling}, but
they provide widely different explanations on the mechanisms of syrinx
generation.  Most researchers, nevertheless, seem to agree on the following
points. First, the syrinx fluid is identical to the CSF, and there should
be some communication between the syrinx and the subarachnoid space. This
point is supported by many studies \cite{ellertsson1969syringomyelia,
ellertsson1969myelocystographic, li1987conventional, heiss2019origin},
although a few different opinions exist \cite{greitz2006unraveling,
koyanagi1997surgical}. Second, some derangement of CSF flow in the spinal
subarachnoid space causes syrinx both in Chiari-I malformation
\cite{wolpert1994chiari, bhadelia1995cerebrospinal, heiss1999elucidating,
hofmann2000phasecontrast, quigley2004cerebrospinal} and subarachnoid
arachnopathy \cite{klekamp1997treatment, brodbelt2003altered,
heiss2012pathophysiology, chang2014dorsal}. The cerebellar tonsils hamper
the CSF flow in the former and adhesive arachnoiditis in the latter.

The problem, however, is where this communicating channel resides and what
mechanism generates the syrinx. On these points, there is no solid
experimental or clinical evidence, and the opinions of researchers deviate
widely. Gardner et al. \cite{gardner1958mechanism} thought that the central
canal intercommunicates the syrinx and the fourth ventricle, and arterial
pressure waves exerted on the central canal generate the syrinx. Williams
et al. also postulated the communication through the central canal, but for
the syrinx generation mechanism, he emphasized the craniospinal pressure
gradient produced by Valsalva maneuver et al
\cite{williams1980pathogenesis}.

On the other hand, Ball and Dayan \cite{ball1972pathogenesis} assumed that
CSF enters the syrinx through the perivascular space of arteries
penetrating the spinal cord. This idea has the following variations. Heiss
et al.  \cite{heiss1999elucidating} proposed that the piston-like movement
of the cerebellar tonsils in Chiari-I patients generates pressure waves in
the spinal subarachnoid space, which subsequently drive CSF into the syrinx
through the perivascular space. Stoodley et al. also considered the
perivascular space as the communicating channel, but he assumed the
arterial pulse pressure as the driving force of CSF
\cite{stoodley2000mechanisms} All these assumptions are not proven and
remain hypothetical. Although the perivascular-space theory seems to be
favored by recent researchers, there remains the possibility that a thin
communicating channel exists between the syrinx and the fourth ventricle
\cite{chang2021hypothesis}.

In our opinion, the main theoretical problems reside in the following
points.
\begin{enumerate}
    \item No theory can explain the pathophysiological mechanism of
syringomyelia in a unified fashion.
    \item No theory can explain how CSF enters from the low-pressure subarachnoid space to the high-pressure syrinx cavity and remains inside.
\end{enumerate}

As to the first point, there are different syringomyelia types, such as
Chiari-I-malformation and spinal-arachnopathy-related
\cite{klekamp1997treatment}. The Chiari-I-malformation-related
syringomyelia is further divided into communicating and non-communicating
\cite{elliott2013syringomyelia}. For each of them, current theories assume
a distinct mechanism of syrinx generation. However, it may be more natural
to conjecture some common mechanism underlying these different types of
syringomyelia \cite{stoodley2000mechanisms}.  The second point is
theoretically essential but challenging to solve. Physical theories dictate
that the expanded syrinx cavity has higher pressure than the subarachnoid
space \cite{serwayr.a.2016fluids, heiss1999elucidating,
davis1989mechanisms, ellertsson1970distending}. Therefore, merely assuming
a communicating channel does not explain how CSF enters the syrinx and
remains inside against this pressure gradient. Even if we take a specific
time window where the subarachnoid pressure exceeds the syrinx pressure, it
does not explain how the CSF remains inside the syrinx after it.

The current article is part of our effort to solve the above theoretical
problems. In our previous paper \cite{chang2021hypothesis}, we hypothesized
that if there is a resistance to CSF flow in a particular direction
(rostral or caudal), it causes a one-way valve-like effect on a CSF channel
inside the spinal cord, leading to the accumulation of CSF and generation
of a syrinx. This hypothesis was attractive to us because it could explain
the pathophysiology of both Chiari-I-malformation-related syringomyelia and
arachnopathy-related syringomyelia. Namely, in
Chiari-I-malformation-related syringomyelia, the herniated cerebellar
tonsils may function as a direction-selective resistance. In
arachnopathy-related syringomyelia, some arachnoid adhesion may play the
same function \cite{chang2014dorsal}.  However, in that article, we just
drew a rough sketch of this process and left out a detailed explanation.
The current article will describe in detail how direction-selective
resistance in the subarachnoid space generates a one-way valve mechanism in
the CSF channel inside the spinal cord.

For this purpose, we used a mathematical model simulating the CSF movement
of the spine---a revised version of our previous model \cite{chang2003hypothesis,
chang2004theoretical}. This model describes the spinal CSF movement as an
electric current in a modeled circuit (a lumped parameter model with
multiple compartments \cite{shi2011review}), and it assumes the existence of a
patent central canal. We placed a direction-selective resistance in this
model at a certain point in the spinal subarachnoid space and observed how
it affects the CSF flow in the central canal.

\section*{Material and Method}

Some problem exists in the computer simulation of the motion of biological
fluids such as blood and CSF. Such bodily fluids move inside flexible
tubes. It, therefore, requires different analysis techniques from those
used in the engineering field, where the boundary of the conduit is
supposed to be solid. For this purpose, researchers widely used lumped
parameter models \cite{shi2011review, @kokalari2013review}. This model
considers the fluid flow inside a flexible tube in analogy to the flow of
electricity in an electric circuit. The accumulation of electricity in a
capacitor represents the expansion of a flexible tube and the accompanying
pressure elevation. An electrical resistor represents the frictional
resistance to flow. This model has a wide variety. For example, it may
model the whole cardiovascular system as one electric circuit, or it may
model it as a synthesis of multiple compartments of electric circuits
[@shi2011review; @kokalari2013review]. Our current model is the type of a
lumped parameter model with multiple compartments.  In this study, we did
not intend to make a quantitatively precise model of the spinal CSF flow
but to make a basic model that reveals the phenomenon underlying the
generation of syringomyelia. For this purpose, we adopted a revised version
of our previous lumped parameter model with multiple compartments.

Previously, we developed a mathematical model that simulated the CSF flow
in the spine \cite{chang2003hypothesis, chang2004theoretical}. This model (a
multiple-compartment version of a 1-dimensional lumped parameter model)
could describe the CSF movement in the whole spine (Figure \ref{fig:model}).

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{ps_circuit_schema.jpg}
    \caption{Schema of the electric circuit model of the CSF dynamics in the
    spine.}
    \label{fig:model}
\end{figure}

A set of differential equations can describe the behavior of this model.
Using computer software, we can numerically calculate its behavior to a
cranial pressure wave (defined as a boundary condition on the cranial
points).  This time, we improved the previous model as follows.

\begin{itemize}
    \item We increased the number of compartments from 10 to 100, thereby making the model more precise.
    \item We estimated the values of the parameters (the capacitance and resistance of each component) of the model as follows so that the model will become more realistic.
        \begin{itemize}
            \item First, we set the length of the modeled spinal cord to be 1 meter.
            \item The resistance of the subarachnoid space ($R$) was
                estimated using the following equations of Poisseuille
                \cite{brook1999numerical, sherwin2003computational, huilgol2020fast}. 
             $$\Delta P=\frac{8\pi \mu{}LQ}{A^{2}}=RQ$$
                \begin{itemize}
                    \item $\Delta P$: Pressure difference between the adjacent compartments
                    \item Q: flow speed per unit surface
                    \item $\mu$: viscosity coefficient. In this case, it was set to the value of water (0.0007).
                    \item L: distance between the adjacent compartments. It was set to 1 cm.
                    \item A: cross sectional area of the subarachnoid
                        space. It was set to the value of a concentric
                        annulus \cite{huilgol2020fast} with the outer diameter of 1cm and the inner diameter of 0.7 cm ($1.6\times{}10^{-4} (m^2)$) 
                \end{itemize}
            \item Thus, $R$ was calculated to be $6872\hspace{0.2cm}(Pa\cdot{}sec/m^3)$
            \item The resistance of the central canal ($r$) was estimated
                using the same equation with $A$ set to
                $\pi{}(10^{-4})^2\hspace{0.1cm}(m^2)$, i.e. the cross
                sectional area of a tube with a diameter of 100 $\mu{}m$.
                Thus, $r$ was calculated to be $1.78\times10^{11}\hspace{0.2cm}(Pa\cdot{}sec/m^3)$
        \end{itemize}
    \item We determined the capacitance ($C_{sub}$)corresponding to the dural elasticity so that the pressure-wave velocity determined by the time constant ($RC$) will roughly correspond to the pressure-wave velocity of the downward CSF wave observed in phase-contrast MRI of normal individuals. Thus, we set $C_{sub}=0.1\hspace{0.2cm}(m^3/Pa\cdot{}sec)$.
\end{itemize}

Figure 1 shows the scheme of the constructed electric circuit model. This
model represents the CSF movement in the spine as electric flow through
multiple compartments of capacitances connected with resistors. Table 1
shows the values of the resistors and capacitors of the system.  A set of
differential equations can describe the behavior of this electric circuit,
and we can solve it numerically by setting the voltage at the cranial nodes
as the boundary condition (Figure \ref{fig:circuit}). In the previous articles
\cite{chang2003hypothesis, chang2004theoretical}, we only analyzed the
transient behavior of the model to a sudden pressure increase on the
cranial side of the subarachnoid space. This analysis helped simulate the
situation of coughing or Valsalva maneuvers. In this article, however, we
analyzed the steady-state response of the model to an oscillating cranial
pressure wave simulating the normal cardiac pulsation of the CSF.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{electric_circuit_new.jpg}
    \caption{Electric circuit diagram representing the CSF dynamics of the spine}
    \label{fig:circuit}
\end{figure}

We numerically solved the differential equations using computer software
(Mathematica version 12, Wolfram Research, Champaign, IL, U.S.A.). We set
the boundary conditions as follows. (1) The voltage at the two cranial
nodes was set to a sine wave oscillating around 100 mmHg with an amplitude
of 20 mmHg at one cycle per second. (2) The initial dural pressure was set
at 100 mmHg in all segments. We set the step of the numerical solution to
1/5000 second and calculated the solution from zero to 20 seconds. We
displayed the obtained solution as a movie in mp4 format.

We analyzed the original normal system and two of its modifications.

\section*{Results}

We present the system's responses as videos. Each video displays either all
or some of the following four values simultaneously: namely, the dural
tension (voltage in D capacitors in Figure 2), the canal tension (voltages
in C capacitors), the subarachnoid CSF flow (flows in R resistors), and the
canal flow (flows in r resistors). We plotted the node position on the
x-axis and the values at that node on the y-axis. The pressure values are
shown in $cmH_2O$, the flows in $ml/sec$. To plot different ranges of
values in a single plot, we multiplied the following values with certain
coefficients: namely, the canal tension with 50, the subarachnoid flow with
0.005, and the canal flow with $1.5\times10^{5}$. We plotted the
rightward flow in the positive and the leftward flow in the negative
direction.  Video 1 shows the original system's response to the sine wave
input on the cranial side. In this condition, CSF makes a smooth to-and-fro
movement in the subarachnoid space with the corresponding pressure wave
along the dura and the central canal. This response corresponds to the CSF
dynamics in a normal individual.

In Video 2, we increased the subarachnoid resistance $R_{25}$ by 20
times, thereby simulating a simple block of the subarachnoid flow in both
directions. In this condition, the dural tension showed a pressure drop at
node 25, corresponding to the increased resistance both in caudal and
rostral flow phases. This pressure drop caused an increase in canal flow in
a direction identical to the subarachnoid CSF flow. This increased canal
flow caused a transient increase in canal pressure distal to the block and
a decrease proximal to the block. However, these pressure changes
alternated according to the flow phase and did not produce a sustained
condition.

In Video 3, we replaced the subarachnoid resistor $R_{25}$
with a one-way valve that selectively resisted flow in the caudal direction
by 50 times. This time, the dural tension curve showed a pressure drop
across node 25, appearing only during the caudal-flow phase. Canal flow
showed alternating increase in caudal and rostral directions according to
the flow phase, which was similar to that in the simple block above.
However, there was a significant difference. Sustained high pressure
appeared in the central canal distal to the valve, and some sustained low
pressure in the segment proximal to the valve. The canal flow near node 25
markedly increased caudally in the caudal-flow phase and rostrally in the
rostral-flow phase. We took out the canal flow and showed it in Video 4.
Observing this video, we can see that the cumulative total of the caudal
flow is larger than that of the rostral flow, and it means that the CSF is
virtually pumped caudally at node 25.

\section*{Discussion}

In this article, we theoretically analyzed the CSF movement in the spinal
cord using a lumped parameter model with multiple components. It simulated
a system with an elastic tube (dura) containing an elastic cylindrical
material (spinal cord) that itself contained a fluid channel (the central
canal). When we placed a direction-selective resistor in the subarachnoid
channel and evoked a to-and-fro pressure wave on this system, it produced a
sustained pressure elevation in the segment distal to the
direction-selective resistor. This phenomenon may explain the pathogenesis
of syringomyelia both in Chiari I malformation and syringomyelia associated
with arachnopathy.

Subarachnoid pressure affects the pressure inside the central canal. As
seen in Figure 2, the absolute pressure inside the central canal is the sum
of the subarachnoid and canal pressure (voltages of $C_k$ and $D_k$ in
electrical terms). Suppose a one-way valve selectively resists caudal flow
in the subarachnoid space at point A, and CSF makes a to-and-fro movement
across it. The caudal-flow phase creates a pressure drop across point A,
making the subarachnoid pressure in the distal segment smaller, and it
reduces the absolute canal pressure in the distal segment. Thus, the
pressure gradient in the central canal across point A increases, which
increases the distal CSF flow in the canal at that point.

On the contrary, the rostral flow does not create a pressure drop. Although
some of the CSF pumped caudally will flow back rostrally, its amount will
be smaller. The net result will be that some CSF is pumped caudally in one
cycle of the to-and-fro movement. Thus, CSF gradually accumulates in the
distal segment of the resistance. We hypothesize that this is the mechanism
underlying the syrinx generation.

This hypothesis solves the theoretical problems pointed out in the
Introduction. A one-way valve in subarachnoid space creates an asymmetry of
the pressure gradient between the caudal and rostral flow phases in the
central canal. This asymmetric alternation of pressure gradient effectively
pumps CSF caudally, creating sustained pressure elevation in the caudal
segment. In other words, the energy of the to-and-fro CSF movement is
translated via the one-way valve into the creation and sustenance of
syringomyelia.

Direction-selective resistance to CSF flow is not an imaginative assumption
but actually exists in patients. In Chiari-I malformation, the herniated
tonsils move like a ball-valve, displaced caudally during the caudal flow
and rostrally during the rostral flow. Higher velocity observed in the
phase-contrast MRI studies suggests that it selectively impedes the caudal
CSF flow more than the cranial flow. This direction-selective resistance
was demonstrated by Williams in direct measurements in Chiari-I patients
and became the basis of his theory \cite{williams1981simultaneous}.

Also, there is a possibility that some types of arachnoid pathology
function as one-way valves. In 2014, we reported a case of thoracic
arachnoid web associated with syringomyelia, in which phase-contrast MRI
detected one-way-valve-like behavior of the arachnoid web
\cite{chang2014dorsal}. We found an obliquely oriented arachnoid web that
reminded us of a one-way valve in surgery. Thus, our hypothesis may also
solve the second theoretical problem that we pointed out in the
Introduction. Namely, we may consider the presence of a one-way valve in
spinal subarachnoid space as a common mechanism underlying both
Chiari-I-related and arachnopathy-related syringomyelia.  Our theory
assumes that the arterial-pulse generated to-and-fro CSF movement provides
the energy for syrinx generation. It is compatible with Stoodley et al.'s
experimental result that syrinx maintenance is dependent on arterial
pulsation \cite{stoodley2000mechanisms}. In this study, the authors showed that

\begin{center}
\includegraphics[width=\textwidth]{pumping_mechanism_close.jpg}
\includegraphics[width=\textwidth]{pumping_mechanism_open.jpg}
\end{center}

\bibliography{my_library}

\end{document}

### 2022-06-30 manuscript/template/main.tex
Changed the multiplication factor of the direction-selective resistance from 50 to 20.

--- 2022-06-30 manuscript/Template for submissions to Scientific Reports/main.tex
@@
 
-The pathophysiology of syringomyelia is still poorly understood. A number
-of hypotheses exist in the literature [@gardner1958mechanism;
-@williams1980pathogenesis; @milhorat1999chiari; @ball1972pathogenesis;
-@klekamp2002pathophysiology; @duboulay1974mechanism; @heiss1999elucidating;
-@milhorat1993anatomical; @stoodley2000pathophysiology; @terae1994increased;
-@chang2003hypothesis; @chang2004theoretical; @greitz2006unraveling], but
-they provide widely different explanations on the mechanisms of syrinx
-generation.  Most researchers, nevertheless, seem to agree on the following
-points. First, the syrinx fluid is identical to the CSF, and there should
-be some communication between the syrinx and the subarachnoid space. This
-point is supported by many studies [@ellertsson1969syringomyelia;
-@ellertsson1969myelocystographic; @li1987conventional; @heiss2019origin],
-although a few different opinions exist [@greitz2006unraveling;
-@koyanagi1997surgical]. Second, some derangement of CSF flow in the spinal
-subarachnoid space causes syrinx both in Chiari-I malformation
-[@wolpert1994chiari; @bhadelia1995cerebrospinal; @heiss1999elucidating;
-@hofmann2000phasecontrast; @quigley2004cerebrospinal] and subarachnoid
-arachnopathy [@klekamp1997treatment; @brodbelt2003altered;
-@heiss2012pathophysiology; @chang2014dorsal]. The cerebellar tonsils hamper
-the CSF flow in the former and adhesive arachnoiditis in the latter.
+The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable).
+The introduction should not include subheadings.
 
-The problem, however, is where this communicating channel resides and what
-mechanism generates the syrinx. On these points, there is no solid
-experimental or clinical evidence, and the opinions of researchers deviate
-widely. Gardner et al. [@gardner1958mechanism] thought that the central
-canal intercommunicates the syrinx and the fourth ventricle, and arterial
-pressure waves exerted on the central canal generate the syrinx. Williams
-et al. also postulated the communication through the central canal, but for
-the syrinx generation mechanism, he emphasized the craniospinal pressure
-gradient produced by Valsalva maneuver et al.  On the other hand, Ball and
-Dayan [@ball1972pathogenesis] assumed that CSF enters the syrinx through
-the perivascular space of arteries penetrating the spinal cord. This idea
-has the following variations. Heiss et al. [@heiss1999elucidating] proposed
-that the piston-like movement of the cerebellar tonsils in Chiari-I
-patients generates pressure waves in the spinal subarachnoid space, which
-subsequently drive CSF into the syrinx through the perivascular space.
-Stoodley et al. also considered the perivascular space as the communicating
-channel, but he assumed the arterial pulse pressure as the driving force of
-CSF [@stoodley2000mechanisms]
+\section*{Results}
 
-All these assumptions are not proven and remain hypothetical. Although the
-perivascular-space theory seems to be favored by recent researchers, there
-remains the possibility that a thin communicating channel exists between
-the syrinx and the fourth ventricle [@chang2021hypothesis].  In our
-opinion, the main theoretical problems reside in the following points.
-\begin{enumerate}
-    \item No theory can explain the pathophysiological mechanism of syringomyelia in a unified fashion.
-    \item No theory can explain how CSF enters from the low-pressure subarachnoid space to the high-pressure syrinx cavity and remains inside.
-\end{enumerate}
+Up to three levels of \textbf{subheading} are permitted. Subheadings should not be numbered.
 
-As to the first point, there are different syringomyelia types, such as
-Chiari-I-malformation and spinal-arachnopathy-related. The
-Chiari-I-malformation-related syringomyelia is further divided into
-communicating and non-communicating. For each of them, current theories
-assume a distinct mechanism of syrinx generation. However, it may be more
-natural to conjecture some common mechanism underlying these different
-types of syringomyelia [@stoodley2000mechanisms].  The second point is
-theoretically essential but challenging to solve. Physical theories dictate
-that the expanded syrinx cavity has higher pressure than the subarachnoid
-space [@serwayr.a.2016fluids; @heiss1999elucidating; @davis1989mechanisms;
-@ellertsson1970distending]. Therefore, merely assuming a communicating
-channel does not explain how CSF enters the syrinx and remains inside
-against this pressure gradient. Even if we take a specific time window
-where the subarachnoid pressure exceeds the syrinx pressure, it does not
-explain how the CSF remains inside the syrinx after it.
+\subsection*{Subsection}
 
-The current article is part of our effort to solve the above theoretical
-problems. In our previous paper [@chang2021hypothesis], we hypothesized
-that if there is a resistance to CSF flow in a particular direction
-(rostral or caudal), it causes a one-way valve-like effect on a CSF channel
-inside the spinal cord, leading to the accumulation of CSF and generation
-of a syrinx. This hypothesis could explain the pathophysiology of both
-Chiari-I-malformation-related syringomyelia and arachnopathy-related
-syringomyelia. In Chiari-I-malformation-related syringomyelia, the
-herniated cerebellar tonsils may function as a direction-selective
-resistance. In arachnopathy-related syringomyelia, some arachnoid adhesion
-may play the same function.  However, in that article, we just drew a rough
-sketch of this process and left out a detailed explanation. The current
-article will describe in detail how direction-selective resistance in the
-subarachnoid space generates a one-way valve mechanism in the CSF channel
-inside the spinal cord.
+Example text under a subsection. Bulleted lists may be used where appropriate, e.g.
 
-For this purpose, we used a mathematical model simulating the CSF movement
-of the spine—a revised version of our previous model [@chang2003hypothesis;
-@chang2004theoretical]. This model describes the spinal CSF movement as an
-electric current in a modeled circuit (a lumped parameter model with
-multiple compartments [@shi2011review]), and it assumes the existence of a
-patent central canal. We placed a direction-selective resistance in this
-model at a certain point in the spinal subarachnoid space and observed how
-it affects the CSF flow in the central canal.  \section*{Results}
+\begin{itemize}
+\item First item
+\item Second item
+\end{itemize}
+
+\subsubsection*{Third-level section}
+
+Topical subheadings are allowed.
 

### 2022-07-12 manuscript/main.tex
minor revision

@@
 \usepackage[T1]{fontenc}
+\usepackage{newfloat}
+\DeclareFloatingEnvironment{video}
 \title{Direction-Selective Resistance to Cerebrospinal-Fluid Flow As
@@
 \keywords{syringomyelia, pathophysiology, simulation}
-
+\input{embed_video.tex}
 \begin{abstract}
@@
     theoretical problem is how cerebrospinal fluid (CSF) enters from
-    low-pressure subarachnoid space to high-pressure syrinx and stays
-    there.
-\end{abstract} \begin{document}
+    low-pressure subarachnoid space to high-pressure syrinx and remains
+    inside the syrinx. We approached this problem with computer simulation
+    of the CSF flow in the spine.
+\end{abstract}
+\begin{document}
 
@@
 
-\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.
-
 \section*{Introduction}
@@
 milhorat1993anatomical, stoodley2000pathophysiology, terae1994increased,
-chang2003hypothesis, chang2004theoretical, greitz2006unraveling}, but
-they provide widely different explanations on the mechanisms of syrinx
-generation.  Most researchers, nevertheless, seem to agree on the following
+chang2003hypothesis, chang2004theoretical, greitz2006unraveling}, but they
+provide widely different explanations on the mechanisms of syrinx
+generation.  Nevertheless, most researchers seem to agree on the following
 points. First, the syrinx fluid is identical to the CSF, and there should
@@
 arachnopathy \cite{klekamp1997treatment, brodbelt2003altered,
-heiss2012pathophysiology, chang2014dorsal}. The cerebellar tonsils hamper
-the CSF flow in the former and adhesive arachnoiditis in the latter.
+heiss2012pathophysiology, chang2014dorsal}. Notably, the cerebellar tonsil
+deranges the CSF flow in the former and adhesive arachnoiditis in the
+latter.
 
@@
 supposed to be solid. For this purpose, researchers widely used lumped
-parameter models \cite{shi2011review, @kokalari2013review}. This model
+parameter models \cite{shi2011review, kokalari2013review}. This model
 considers the fluid flow inside a flexible tube in analogy to the flow of
@@
 model it as a synthesis of multiple compartments of electric circuits
-[@shi2011review; @kokalari2013review]. Our current model is the type of a
+\cite{shi2011review, kokalari2013review}. Our current model is the type of a
 lumped parameter model with multiple compartments.  In this study, we did
@@
 \begin{itemize}
-    \item We increased the number of compartments from 10 to 100, thereby making the model more precise.
-    \item We estimated the values of the parameters (the capacitance and resistance of each component) of the model as follows so that the model will become more realistic.
+    \item We increased the number of compartments from 10 to 100,
+        thereby making the model more precise.
+    \item We estimated the values of the parameters
+        (the capacitance and resistance of each component)
+        of the model as follows so that the model will become more realistic.
         \begin{itemize}
@@
 
-We analyzed the original normal system and two of its modifications.
+We analyzed the original normal system and two of its modifications. In the
+first modification, we simply increased the subarachnoid resistance at
+point 25 ($R_{25}$) by 20 times. In the second modification, we placed a
+direction-selective subarachnoid resistance at point 25, so that only the
+resistance to the caudal flow would be increased by 20 times.
 
@@
 
-We present the system's responses as videos. Each video displays either all
-or some of the following four values simultaneously: namely, the dural
-tension (voltage in D capacitors in Figure 2), the canal tension (voltages
-in C capacitors), the subarachnoid CSF flow (flows in R resistors), and the
-canal flow (flows in r resistors). We plotted the node position on the
-x-axis and the values at that node on the y-axis. The pressure values are
-shown in $cmH_2O$, the flows in $ml/sec$. To plot different ranges of
-values in a single plot, we multiplied the following values with certain
-coefficients: namely, the canal tension with 50, the subarachnoid flow with
-0.005, and the canal flow with $1.5\times10^{5}$. We plotted the
-rightward flow in the positive and the leftward flow in the negative
-direction.  Video 1 shows the original system's response to the sine wave
-input on the cranial side. In this condition, CSF makes a smooth to-and-fro
-movement in the subarachnoid space with the corresponding pressure wave
-along the dura and the central canal. This response corresponds to the CSF
-dynamics in a normal individual.
+We present the systems' responses to twenty cycles of to-and-fro waves as
+animations. The x-axis of each animation represents the 100 nodes of the
+circuit laid out from the cranial to caudal direction. The y-axis displays
+some of the following four measures: the dural tension (voltage in D
+capacitors in Figure 2), the canal tension (voltages in C capacitors), the
+subarachnoid CSF flow (flows in R resistors), and the canal flow (flows in
+r resistors). We plotted the caudal flow in the positive and the rostral
+flow in the negative direction. The pressure values are shown in $cmH_2O$,
+the flows in $ml/sec$. To plot the four measures in a single animation, we
+multiplied the following three measures---the canal tension, the
+subarachnoid CSF flow, and the canal flow---with the following
+coefficients, respectively: namely, the canal tension with 50, the
+subarachnoid flow with 0.005, and the canal flow with $1.5\times10^{5}$.
 
-In Video 2, we increased the subarachnoid resistance $R_{25}$ by 20
-times, thereby simulating a simple block of the subarachnoid flow in both
-directions. In this condition, the dural tension showed a pressure drop at
-node 25, corresponding to the increased resistance both in caudal and
-rostral flow phases. This pressure drop caused an increase in canal flow in
-a direction identical to the subarachnoid CSF flow. This increased canal
-flow caused a transient increase in canal pressure distal to the block and
-a decrease proximal to the block. However, these pressure changes
-alternated according to the flow phase and did not produce a sustained
-condition.
+Video \ref{video:norm} shows the original system's response representing
+the normal condition. In this state, CSF makes a smooth to-and-fro movement
+in the subarachnoid space with the corresponding pressure wave along the
+dura and the central canal. CSF also makes to-and-fro movements in the
+canal.
 
-In Video 3, we replaced the subarachnoid resistor $R_{25}$
-with a one-way valve that selectively resisted flow in the caudal direction
-by 50 times. This time, the dural tension curve showed a pressure drop
-across node 25, appearing only during the caudal-flow phase. Canal flow
-showed alternating increase in caudal and rostral directions according to
-the flow phase, which was similar to that in the simple block above.
-However, there was a significant difference. Sustained high pressure
-appeared in the central canal distal to the valve, and some sustained low
-pressure in the segment proximal to the valve. The canal flow near node 25
-markedly increased caudally in the caudal-flow phase and rostrally in the
-rostral-flow phase. We took out the canal flow and showed it in Video 4.
-Observing this video, we can see that the cumulative total of the caudal
-flow is larger than that of the rostral flow, and it means that the CSF is
-virtually pumped caudally at node 25.
+\begin{video}[hbt]
+    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_norm.jpg}}{totalAnimationNorm.mp4}
+    \caption{Video showing the normal circuit response}
+    \label{video:norm}
+\end{video}
+
+In Video \ref{video:simple_block}, we increased the subarachnoid resistance
+$R_{25}$ by 20 times, thereby simulating a simple block of the subarachnoid
+flow in both directions. In this condition, both the caudal and rostral
+flow along the resistance produced a drop of the dural tension downstream
+to the resistance, corresponding to the increased resistance both in the
+caudal and rostral flow phases. This pressure drop caused an increase in
+canal flow in the same direction as the subarachnoid flow. This increased
+canal flow caused a transient increase in the canal pressure distal to the
+block and a decrease proximal to the block. However, these pressure changes
+alternated along the alternation of the flow direction and did not produce
+a sustained pressure increase.
+
+\begin{video}[hbt]
+    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_simple_block.jpg}}{totalAnimationSb.mp4}
+    \caption{Video showing the response of the circuit with a simple
+    resistor at point 25}
+    \label{video:simple_block}
+\end{video}
+
+\begin{video}[hbt]
+    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{totalAnimation.mp4}
+    \caption{Video showing the response of the circuit with a
+    direction-selective resistor at point 25}
+    \label{video:oneway}
+\end{video}
+
+\begin{video}[hbt]
+    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowOneway.mp4}
+    \caption{Video showing the canal flow in the model with
+    direction-selective resistance at point 25}
+    \label{video:canal_flow_oneway}
+\end{video}
+
+\begin{video}[hbt]
+    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowComparison.mp4}
+    \caption{Video showing the canal flow in the two models: simple
+    resistance at point 25 and direction-selective resistance at point 25}
+    \label{video:canal_comparison}
+\end{video}
+
+In Video \ref{video:oneway}, we replaced the subarachnoid resistor $R_{25}$
+with a direction-selective resistor whose resistance to the rostral flow
+was unchanged but that to the caudal flow was increased by 20 times.  This
+time, as shown in Video \ref{video:oneway}, sustained high pressure
+appeared in the central canal in the segment distal to the replaced
+resistor, and sustained low pressure in the segment proximal to it.  This
+sustained pressure gradually accumulated as the flow cycle proceeded.  The
+dural tension showed a pressure drop at node 25 only during the caudal-flow
+phase.  The to-and-fro canal flow increased near the node 25 similarly to
+that in the simple block above, but, this time, the increase was larger in
+the caudal direction.
+
+We took out the canal flow and showed it in Video 4.  Observing this video,
+we can see that the cumulative total of the caudal flow is larger than that
+of the rostral flow, and it means that the CSF is virtually pumped caudally
+at node 25. To further elucidate this point, we plotted the canal flow in
+the simple block as shown in Video \ref{video:simple_block} and that in the
+one-way block as shown in Video \ref{video:oneway}. We can clearly see in
+this video that the caudal flow in the canal is
 
@@
 a system with an elastic tube (dura) containing an elastic cylindrical
-material (spinal cord) that itself contained a fluid channel (the central
+material (spinal cord) that itself had a fluid channel inside (the central
 canal). When we placed a direction-selective resistor in the subarachnoid
-channel and evoked a to-and-fro pressure wave on this system, it produced a
+space and evoked a to-and-fro pressure wave on this system, it produced a
 sustained pressure elevation in the segment distal to the
@@
 Subarachnoid pressure affects the pressure inside the central canal. As
-seen in Figure 2, the absolute pressure inside the central canal is the sum
-of the subarachnoid and canal pressure (voltages of $C_k$ and $D_k$ in
-electrical terms). Suppose a one-way valve selectively resists caudal flow
-in the subarachnoid space at point A, and CSF makes a to-and-fro movement
-across it. The caudal-flow phase creates a pressure drop across point A,
-making the subarachnoid pressure in the distal segment smaller, and it
-reduces the absolute canal pressure in the distal segment. Thus, the
-pressure gradient in the central canal across point A increases, which
-increases the distal CSF flow in the canal at that point.
+seen in Figure \ref{fig:circuit}, the absolute pressure inside the central
+canal is the sum of the subarachnoid and canal pressure (voltages of $C_k$
+and $D_k$ in electrical terms). Suppose a one-way valve selectively resists
+caudal flow in the subarachnoid space at point A. Caudal CSF flow creates a
+pressure drop across this valve, with the distal pressure smaller than the
+proximal one. It decreases the absolute canal pressure distal to point A
+because it is the sum of the subarachnoid pressure and the canal pressure.
+It, therefore, creates a pressure gradient in the central canal across
+point A, thereby increasing the distal CSF flow in the canal at that point
+(Figure \ref{fig:pump_close}).
 
-On the contrary, the rostral flow does not create a pressure drop. Although
-some of the CSF pumped caudally will flow back rostrally, its amount will
-be smaller. The net result will be that some CSF is pumped caudally in one
-cycle of the to-and-fro movement. Thus, CSF gradually accumulates in the
-distal segment of the resistance. We hypothesize that this is the mechanism
-underlying the syrinx generation.
+\begin{figure}[hbt]
+    \centering
+    \includegraphics[width=\textwidth]{pumping_mechanism_close.jpg}
+    \caption{Increased central-canal flow across a direction-selective
+    resistance in the subarachnoid space}
+    \label{fig:pump_close}
+\end{figure}
+
+On the contrary, reverse flow, not encountering resistance, does not create
+a pressure drop (Figure \ref{fig:pump_open}). Although some of the CSF that
+had been pumped caudally during the caudal-flow phase will flow back
+rostrally, its amount will be smaller. The net result will be that some CSF
+is pumped caudally in one cycle of the to-and-fro movement. Thus, CSF
+gradually accumulates in the distal segment of the resistance (Video 3). We
+hypothesize that this is the mechanism underlying the syrinx generation.
+
+\begin{figure}[hbt]
+    \centering
+    \includegraphics[width=\textwidth]{pumping_mechanism_open.jpg}
+    \caption{Normal central-canal flow across a direction-selective
+    resistance during the reverse flow}
+    \label{fig:pump_open}
+\end{figure}
 
@@
 
-\begin{center}
-\includegraphics[width=\textwidth]{pumping_mechanism_close.jpg}
-\includegraphics[width=\textwidth]{pumping_mechanism_open.jpg}
-\end{center}
-
 \bibliography{my_library}

### 2022-07-23 manuscript/main.tex
Revision of manuscript/main.tex

@@
 \title{Direction-Selective Resistance to Cerebrospinal-Fluid Flow As
-the Mechanism of Syrinx Generation in Syringomyelia}
+the Generative Mechanism of Syringomyelia}
 
@@
 \begin{abstract}
+
     The pathophysiology of syringomyelia is not well understood. The main
-    theoretical problem is how cerebrospinal fluid (CSF) enters from
-    low-pressure subarachnoid space to high-pressure syrinx and remains
-    inside the syrinx. We approached this problem with computer simulation
-    of the CSF flow in the spine.
+    theoretical problem unaddressed by previous hypotheses is how
+    cerebrospinal fluid (CSF) enters from low-pressure subarachnoid space
+    to high-pressure syrinx and remains inside. We approached this problem
+    with a computer simulation of the CSF flow in the spine. We
+    hypothesized that to-and-fro movement of CSF across a
+    direction-selective resistance, via the pressure drop caused by the
+    resistance, pumps the CSF in the intraspinal channel distally.
+
+    We constructed a model of CSF dynamics in the spine, which was an
+    electric circuit based on a lumped parameter model with multiple
+    compartments. The model assumed a CSF channel inside the spinal cord.
+    With this model, we could analyze the to-and-fro CSF movement of the
+    spine. We then created a direction-selective resistance in the
+    subarachnoid space. We changed a subarachnoid resistor so that it would
+    resist only to the caudally-directed flow.
+
+    In the caudal flow phase, flow across the replaced resistor produced a
+    pressure drop in the distal subarachnoid segment. It subsequently
+    decreased the spinal-channel pressure in the distal segment; thus, the
+    pressure gradient across the point increased. This increased pressure
+    gradient pumped the CSF in the channel caudally. Because this
+    phenomenon did not occur in the rostral flow phase, the rostral flow in
+    the channel during this phase was smaller.  Overall, each cycle of
+    to-and-fro CSF movement pumped some CSF caudally in the spinal channel.
+
+    We could reasonably hypothesize that to-and-fro CSF movement across a
+    direction-selective resistance was the generative mechanism of
+    syringomyelia.
+
 \end{abstract}
@@
 
-The pathophysiology of syringomyelia is still poorly understood. A number
-of hypotheses exist in the literature \cite{gardner1958mechanism,
+The pathophysiology of syringomyelia is still poorly understood. Many
+hypotheses exist in the literature \cite{gardner1958mechanism,
 williams1980pathogenesis, milhorat1999chiari, ball1972pathogenesis,
@@
 provide widely different explanations on the mechanisms of syrinx
-generation.  Nevertheless, most researchers seem to agree on the following
-points. First, the syrinx fluid is identical to the CSF, and there should
-be some communication between the syrinx and the subarachnoid space. This
-point is supported by many studies \cite{ellertsson1969syringomyelia,
+generation. We may, however, enumerate what few consensuses as follows.
+First, the syrinx fluid is identical to the CSF, and there is some
+communication between the syrinx and the subarachnoid space. Many studies
+support this point \cite{ellertsson1969syringomyelia,
 ellertsson1969myelocystographic, li1987conventional, heiss2019origin},
-although a few different opinions exist \cite{greitz2006unraveling,
+albeit some different opinions \cite{greitz2006unraveling,
 koyanagi1997surgical}. Second, some derangement of CSF flow in the spinal
@@
 mechanism generates the syrinx. On these points, there is no solid
-experimental or clinical evidence, and the opinions of researchers deviate
+experimental or clinical evidence, and the opinions of researchers vary
 widely. Gardner et al. \cite{gardner1958mechanism} thought that the central
-canal intercommunicates the syrinx and the fourth ventricle, and arterial
-pressure waves exerted on the central canal generate the syrinx. Williams
-et al. also postulated the communication through the central canal, but for
-the syrinx generation mechanism, he emphasized the craniospinal pressure
-gradient produced by Valsalva maneuver et al
-\cite{williams1980pathogenesis}.
+canal intercommunicates the syrinx and the fourth ventricle. Arterial
+pulses then exert pressure waves on the central canal and generate the
+syrinx. Williams et al. also postulated the communication through the
+central canal. He, however, emphasized the craniospinal pressure gradient
+produced by Valsalva maneuver et al. \cite{williams1980pathogenesis}.
 
 On the other hand, Ball and Dayan \cite{ball1972pathogenesis} assumed that
-CSF enters the syrinx through the perivascular space of arteries
+CSF entered the syrinx through the perivascular space of arteries
 penetrating the spinal cord. This idea has the following variations. Heiss
 et al.  \cite{heiss1999elucidating} proposed that the piston-like movement
-of the cerebellar tonsils in Chiari-I patients generates pressure waves in
-the spinal subarachnoid space, which subsequently drive CSF into the syrinx
-through the perivascular space. Stoodley et al. also considered the
+of the cerebellar tonsils in Chiari-I patients generated pressure waves in
+the spinal subarachnoid space. And it subsequently drove CSF into the
+syrinx through the perivascular space. Stoodley et al. also considered the
 perivascular space as the communicating channel, but he assumed the
-arterial pulse pressure as the driving force of CSF
-\cite{stoodley2000mechanisms} All these assumptions are not proven and
-remain hypothetical. Although the perivascular-space theory seems to be
-favored by recent researchers, there remains the possibility that a thin
-communicating channel exists between the syrinx and the fourth ventricle
-\cite{chang2021hypothesis}.
+arterial pulse pressure as the driving force \cite{stoodley2000mechanisms}.
+All these assumptions are not proven and remain hypothetical. Although
+recent researchers seem to favor the perivascular-space theory, there
+remains the possibility that a thin communicating channel exists between
+the syrinx and the fourth ventricle \cite{chang2021hypothesis}.
 
@@
 syringomyelia is further divided into communicating and non-communicating
-\cite{elliott2013syringomyelia}. For each of them, current theories assume
-a distinct mechanism of syrinx generation. However, it may be more natural
-to conjecture some common mechanism underlying these different types of
-syringomyelia \cite{stoodley2000mechanisms}.  The second point is
-theoretically essential but challenging to solve. Physical theories dictate
-that the expanded syrinx cavity has higher pressure than the subarachnoid
-space \cite{serwayr.a.2016fluids, heiss1999elucidating,
-davis1989mechanisms, ellertsson1970distending}. Therefore, merely assuming
-a communicating channel does not explain how CSF enters the syrinx and
-remains inside against this pressure gradient. Even if we take a specific
-time window where the subarachnoid pressure exceeds the syrinx pressure, it
-does not explain how the CSF remains inside the syrinx after it.
+\cite{elliott2013syringomyelia}. Current theories cannot explain these
+different types of syringomyelia in a unified fashion. However, it may be
+more natural to conjecture some common mechanism underlying these different
+types of syringomyelia \cite{stoodley2000mechanisms}. The second point is
+theoretically essential but challenging. Physical laws dictate that the
+expanded syrinx cavity has higher pressure than the subarachnoid space
+\cite{serwayr.a.2016fluids, heiss1999elucidating, davis1989mechanisms,
+ellertsson1970distending}, which is understandable considering the elastic
+tension of the syrinx wall that the inside pressure confront. Therefore,
+merely assuming a communicating channel does not explain how CSF enters the
+syrinx against this pressure gradient and remains inside. Even if we take a
+specific time window where the subarachnoid pressure exceeds the syrinx
+pressure, it does not explain how the CSF remains inside the syrinx after
+it.
 
 The current article is part of our effort to solve the above theoretical
-problems. In our previous paper \cite{chang2021hypothesis}, we hypothesized
-that if there is a resistance to CSF flow in a particular direction
-(rostral or caudal), it causes a one-way valve-like effect on a CSF channel
-inside the spinal cord, leading to the accumulation of CSF and generation
-of a syrinx. This hypothesis was attractive to us because it could explain
-the pathophysiology of both Chiari-I-malformation-related syringomyelia and
-arachnopathy-related syringomyelia. Namely, in
-Chiari-I-malformation-related syringomyelia, the herniated cerebellar
-tonsils may function as a direction-selective resistance. In
-arachnopathy-related syringomyelia, some arachnoid adhesion may play the
-same function \cite{chang2014dorsal}.  However, in that article, we just
-drew a rough sketch of this process and left out a detailed explanation.
-The current article will describe in detail how direction-selective
-resistance in the subarachnoid space generates a one-way valve mechanism in
-the CSF channel inside the spinal cord.
+problems. We proposed in our previous paper \cite{chang2021hypothesis} a
+hypothesis on the pathophysiology of syringomyelia. We hypothesized that a
+direction-selective resistance to spinal subarachnoid CSF flow causes
+syringomyelia. Suppose there is a resistance to spinal CSF flow only in
+the, e.g., caudal direction. To-and-fro CSF movement across it will pump
+CSF in an intraspinal channel caudally, causing syringomyelia. This
+hypothesis could solve the two problems discussed above. It could solve the
+paradox of CSF movement against the pressure gradient. Also, it could
+explain the pathophysiology of both Chiari-I-malformation-related
+syringomyelia and arachnopathy-related syringomyelia. The herniated
+cerebellar tonsils function as the selective resistance in Chiari-I
+malformation. And some arachnoid valve plays that role in
+arachnopathy-related syringomyelia \cite{chang2014dorsal}. However, in that
+article, we just drew a rough sketch of this process and left out a
+detailed explanation. The current article will describe this mechanism in
+detail using computer simulation.
 
 For this purpose, we used a mathematical model simulating the CSF movement
-of the spine---a revised version of our previous model \cite{chang2003hypothesis,
-chang2004theoretical}. This model describes the spinal CSF movement as an
-electric current in a modeled circuit (a lumped parameter model with
-multiple compartments \cite{shi2011review}), and it assumes the existence of a
-patent central canal. We placed a direction-selective resistance in this
-model at a certain point in the spinal subarachnoid space and observed how
-it affects the CSF flow in the central canal.
+of the spine. We revised a lumped parameter model with multiple
+compartments used in our previous articles \cite{chang2003hypothesis,
+chang2004theoretical}.  We placed a direction-selective resistance in this
+model at a certain point in the spinal subarachnoid space. We then observed
+how it affected the CSF flow in the channel inside the spinal cord.
 
@@
 fluids such as blood and CSF. Such bodily fluids move inside flexible
-tubes. It, therefore, requires different analysis techniques from those
-used in the engineering field, where the boundary of the conduit is
-supposed to be solid. For this purpose, researchers widely used lumped
-parameter models \cite{shi2011review, kokalari2013review}. This model
-considers the fluid flow inside a flexible tube in analogy to the flow of
-electricity in an electric circuit. The accumulation of electricity in a
-capacitor represents the expansion of a flexible tube and the accompanying
-pressure elevation. An electrical resistor represents the frictional
-resistance to flow. This model has a wide variety. For example, it may
-model the whole cardiovascular system as one electric circuit, or it may
-model it as a synthesis of multiple compartments of electric circuits
-\cite{shi2011review, kokalari2013review}. Our current model is the type of a
-lumped parameter model with multiple compartments.  In this study, we did
-not intend to make a quantitatively precise model of the spinal CSF flow
-but to make a basic model that reveals the phenomenon underlying the
-generation of syringomyelia. For this purpose, we adopted a revised version
-of our previous lumped parameter model with multiple compartments.
+tubes. It differs from the usual situation of fluid mechanics, where the
+boundary of the fluid conduit is solid. Thus, we cannot simply apply the
+standard Navier-Stokes equations for our simulation. For this reason,
+researchers have commonly used lumped parameter models \cite{shi2011review,
+kokalari2013review}. This model considers the fluid flow inside a flexible
+tube analogous to the electric flow in an electric circuit. The
+accumulation of electricity in a capacitor represents the expansion of a
+flexible tube and the accompanying pressure elevation. An electrical
+resistor represents the frictional resistance to flow. This model has a
+wide variety. For example, it may model the whole cardiovascular system as
+one electric circuit, or it may model it as a synthesis of multiple
+compartments of electric circuits \cite{shi2011review, kokalari2013review}.
+Our current model is the type of lumped parameter model with multiple
+compartments that simulates the CSF dynamics in the spine and is an updated
+version of the model used in our previous articles
+\cite{chang2003hypothesis, chang2004theoretical}. In this study, we did not
+intend to make a quantitatively precise model of the spinal CSF flow but to
+make a basic model that reveals the phenomenon underlying the generation of
+syringomyelia.
 
@@
 multiple-compartment version of a 1-dimensional lumped parameter model)
-could describe the CSF movement in the whole spine (Figure \ref{fig:model}).
+could describe the CSF movement in the whole spine (Figure
+\ref{fig:model}). In this model, the \textit{D} capacitors represented the
+dural tension, \textit{C} capacitors the tension of the central canal,
+\textit{R} resistors the frictional resistance in the subarachnoid space,
+and \textit{r} resistors the frictional resistance in the central canal.
 
@@
 
-A set of differential equations can describe the behavior of this model.
-Using computer software, we can numerically calculate its behavior to a
-cranial pressure wave (defined as a boundary condition on the cranial
-points).  This time, we improved the previous model as follows.
+Figure \ref{fig:circuit} shows the bare electric circuit extracted from
+Figure \ref{fig:model}. A set of differential equations could describe the
+behavior of this model.  Using computer software, we could numerically
+calculate its behavior in response to a certain cranial pressure wave
+(defined as a boundary condition on the cranial nodes). This time, we
+improved the previous model as follows.
 
@@
         thereby making the model more precise.
-    \item We estimated the values of the parameters
+    \item We revised the values of the parameters
         (the capacitance and resistance of each component)
@@
 
-Figure 1 shows the scheme of the constructed electric circuit model. This
-model represents the CSF movement in the spine as electric flow through
-multiple compartments of capacitances connected with resistors. Table 1
-shows the values of the resistors and capacitors of the system.  A set of
-differential equations can describe the behavior of this electric circuit,
-and we can solve it numerically by setting the voltage at the cranial nodes
-as the boundary condition (Figure \ref{fig:circuit}). In the previous articles
-\cite{chang2003hypothesis, chang2004theoretical}, we only analyzed the
-transient behavior of the model to a sudden pressure increase on the
-cranial side of the subarachnoid space. This analysis helped simulate the
-situation of coughing or Valsalva maneuvers. In this article, however, we
-analyzed the steady-state response of the model to an oscillating cranial
+Figure \ref{fig:model} shows the scheme of the constructed electric circuit
+model. This model represents the CSF movement in the spine as electric flow
+through multiple compartments of capacitances connected with resistors.
+Table 1 shows the values of the resistors and capacitors of the system. A
+set of differential equations can describe the behavior of this electric
+circuit, and we can solve it numerically by setting the voltage at the
+cranial nodes as the boundary condition (Figure \ref{fig:circuit}). In the
+previous articles \cite{chang2003hypothesis, chang2004theoretical}, we only
+analyzed the transient behavior of the model to a sudden pressure increase
+on the cranial side of the subarachnoid space. This analysis helped
+simulate the situation of coughing or Valsalva maneuvers. In this article,
+however, we analyzed the response of the model to an oscillating cranial
 pressure wave simulating the normal cardiac pulsation of the CSF.
@@
 We numerically solved the differential equations using computer software
-(Mathematica version 12, Wolfram Research, Champaign, IL, U.S.A.). We set
-the boundary conditions as follows. (1) The voltage at the two cranial
-nodes was set to a sine wave oscillating around 100 mmHg with an amplitude
-of 20 mmHg at one cycle per second. (2) The initial dural pressure was set
-at 100 mmHg in all segments. We set the step of the numerical solution to
-1/5000 second and calculated the solution from zero to 20 seconds. We
-displayed the obtained solution as a movie in mp4 format.
+(Mathematica version 12, Wolfram Research, Champaign, IL, U.S.A.) on a
+personal computer. We set the boundary conditions as follows. (1) The
+voltage at the two cranial nodes was set to a sine wave oscillating around
+10 $cmH_{2}O$ with an amplitude of 20 $cmH_{2}O$ at one cycle per second.
+(2) The initial dural pressure was set at 10 $cmH_{2}O$ in all segments. We
+set the step of the numerical solution to 1/5000 second and calculated the
+solution from zero to 20 seconds. We displayed the obtained solution as a
+movie in mp4 format.
 
@@
 
-We present the systems' responses to twenty cycles of to-and-fro waves as
-animations. The x-axis of each animation represents the 100 nodes of the
-circuit laid out from the cranial to caudal direction. The y-axis displays
-some of the following four measures: the dural tension (voltage in D
-capacitors in Figure 2), the canal tension (voltages in C capacitors), the
-subarachnoid CSF flow (flows in R resistors), and the canal flow (flows in
-r resistors). We plotted the caudal flow in the positive and the rostral
-flow in the negative direction. The pressure values are shown in $cmH_2O$,
-the flows in $ml/sec$. To plot the four measures in a single animation, we
-multiplied the following three measures---the canal tension, the
-subarachnoid CSF flow, and the canal flow---with the following
+We present the systems' responses in animations showing twenty cycles of
+to-and-fro waves. The x-axis of each animation represents the 100 nodes of
+the circuit laid out from the cranial to caudal direction. The y-axis
+displays some of the following four measures: the dural tension (voltage in
+D capacitors in Figure 2), the canal tension (voltages in C capacitors),
+the subarachnoid CSF flow (flows in R resistors), and the channel flow
+(flows in r resistors). We plotted the caudal flow in the positive and the
+rostral flow in the negative direction. The pressure values are shown in
+$cmH_2O$, the flows in $ml/sec$. To plot the four measures in a single
+animation, we multiplied the following three measures---the canal tension,
+the subarachnoid CSF flow, and the canal flow---with the following
 coefficients, respectively: namely, the canal tension with 50, the
@@
 Video \ref{video:norm} shows the original system's response representing
-the normal condition. In this state, CSF makes a smooth to-and-fro movement
+the normal condition. In this state, CSF made a smooth to-and-fro movement
 in the subarachnoid space with the corresponding pressure wave along the
-dura and the central canal. CSF also makes to-and-fro movements in the
-canal.
+dura and the central canal. CSF also made smooth to-and-fro movements in
+the channel.
 
-\begin{video}[hbt]
-    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_norm.jpg}}{totalAnimationNorm.mp4}
-    \caption{Video showing the normal circuit response}
-    \label{video:norm}
-\end{video}
+%\begin{video}[hbt]
+%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_norm.jpg}}{totalAnimationNorm.mp4}
+%    \caption{Video showing the normal circuit response}
+%    \label{video:norm}
+%\end{video}
 
@@
 flow in both directions. In this condition, both the caudal and rostral
-flow along the resistance produced a drop of the dural tension downstream
-to the resistance, corresponding to the increased resistance both in the
-caudal and rostral flow phases. This pressure drop caused an increase in
-canal flow in the same direction as the subarachnoid flow. This increased
-canal flow caused a transient increase in the canal pressure distal to the
-block and a decrease proximal to the block. However, these pressure changes
-alternated along the alternation of the flow direction and did not produce
-a sustained pressure increase.
+flow across the resistance produced pressure drop in the distal
+subarachnoid segment.  This pressure drop caused an increase in canal flow
+in the same direction as the subarachnoid flow. This increased canal flow
+caused a transient increase in the canal pressure distal to the block and a
+decrease proximal to the block. However, these pressure changes alternated
+along the alternation of the flow direction and did not produce a sustained
+pressure increase.
 
-\begin{video}[hbt]
-    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_simple_block.jpg}}{totalAnimationSb.mp4}
-    \caption{Video showing the response of the circuit with a simple
-    resistor at point 25}
-    \label{video:simple_block}
-\end{video}
+%\begin{video}[hbt]
+%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_simple_block.jpg}}{totalAnimationSb.mp4}
+%    \caption{Video showing the response of the circuit with a simple
+%    resistor at point 25}
+%    \label{video:simple_block}
+%\end{video}
+%
+%\begin{video}[hbt]
+%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{totalAnimation.mp4}
+%    \caption{Video showing the response of the circuit with a
+%    direction-selective resistor at point 25}
+%    \label{video:oneway}
+%\end{video}
 
-\begin{video}[hbt]
-    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{totalAnimation.mp4}
-    \caption{Video showing the response of the circuit with a
-    direction-selective resistor at point 25}
-    \label{video:oneway}
-\end{video}
-
-\begin{video}[hbt]
-    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowOneway.mp4}
-    \caption{Video showing the canal flow in the model with
-    direction-selective resistance at point 25}
-    \label{video:canal_flow_oneway}
-\end{video}
-
-\begin{video}[hbt]
-    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowComparison.mp4}
-    \caption{Video showing the canal flow in the two models: simple
-    resistance at point 25 and direction-selective resistance at point 25}
-    \label{video:canal_comparison}
-\end{video}
+%\begin{video}[hbt]
+%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowOneway.mp4}
+%    \caption{Video showing the canal flow in the model with
+%    direction-selective resistance at point 25}
+%    \label{video:canal_flow_oneway}
+%\end{video}
+%
+%\begin{video}[hbt]
+%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowComparison.mp4}
+%    \caption{Video showing the canal flow in the two models: simple
+%    resistance at point 25 and direction-selective resistance at point 25}
+%    \label{video:canal_comparison}
+%\end{video}
 
@@
 
-In this article, we theoretically analyzed the CSF movement in the spinal
-cord using a lumped parameter model with multiple components. It simulated
-a system with an elastic tube (dura) containing an elastic cylindrical
-material (spinal cord) that itself had a fluid channel inside (the central
-canal). When we placed a direction-selective resistor in the subarachnoid
-space and evoked a to-and-fro pressure wave on this system, it produced a
-sustained pressure elevation in the segment distal to the
-direction-selective resistor. This phenomenon may explain the pathogenesis
-of syringomyelia both in Chiari I malformation and syringomyelia associated
-with arachnopathy.
+In this article, we theoretically analyzed the CSF movement in the spine
+using a lumped parameter model with multiple components. It simulated a
+system with an elastic tube (dura) containing an elastic cylindrical
+material (spinal cord) that itself had a fluid channel inside (e.g. the
+central canal). When we placed a direction-selective resistor in the
+subarachnoid space and evoked a to-and-fro pressure wave on this system, it
+produced a sustained pressure elevation in the segment distal to the
+resistor in the resisted direction. This phenomenon may explain the
+pathogenesis of syringomyelia both in Chiari I malformation and
+syringomyelia associated with arachnopathy.
 
-Subarachnoid pressure affects the pressure inside the central canal. As
-seen in Figure \ref{fig:circuit}, the absolute pressure inside the central
-canal is the sum of the subarachnoid and canal pressure (voltages of $C_k$
-and $D_k$ in electrical terms). Suppose a one-way valve selectively resists
-caudal flow in the subarachnoid space at point A. Caudal CSF flow creates a
-pressure drop across this valve, with the distal pressure smaller than the
-proximal one. It decreases the absolute canal pressure distal to point A
-because it is the sum of the subarachnoid pressure and the canal pressure.
-It, therefore, creates a pressure gradient in the central canal across
-point A, thereby increasing the distal CSF flow in the canal at that point
-(Figure \ref{fig:pump_close}).
+Subarachnoid pressure pushes the spinal cord material and affects the
+pressure inside the central canal. As seen in Figure \ref{fig:circuit}, the
+absolute pressure inside the central canal is the sum of the subarachnoid
+and canal tension (voltages of $C_k$ and $D_k$ in electrical terms).
+Suppose a one-way valve selectively resists caudal flow in the subarachnoid
+space at point $A$. Caudal CSF flow creates a pressure drop across point
+$A$, with the caudal pressure smaller than the proximal one. Thus, the
+absolute pressure in the canal distal to point $A$ become smaller because
+the outside subarachnoid pressure there is smaller. It, therefore, creates
+a pressure gradient in the central canal across point $A$, thereby
+increasing the distal CSF flow in the canal at that point (Figure
+\ref{fig:pump_close}).
 
@@
 
-On the contrary, reverse flow, not encountering resistance, does not create
+On the contrary, rostral flow, not encountering resistance, does not create
 a pressure drop (Figure \ref{fig:pump_open}). Although some of the CSF that
@@
 
-This hypothesis solves the theoretical problems pointed out in the
-Introduction. A one-way valve in subarachnoid space creates an asymmetry of
-the pressure gradient between the caudal and rostral flow phases in the
-central canal. This asymmetric alternation of pressure gradient effectively
-pumps CSF caudally, creating sustained pressure elevation in the caudal
-segment. In other words, the energy of the to-and-fro CSF movement is
-translated via the one-way valve into the creation and sustenance of
-syringomyelia.
+This theory successfully explains how CSF is pumped against the pressure
+gradient and remains inside the syrinx, one of the problems pointed out in
+the Introduction. A one-way valve in subarachnoid space creates an
+asymmetry of the pressure gradient between the caudal and rostral flow
+phases in the central canal. This asymmetric alternation of pressure
+gradient effectively pumps CSF caudally, creating sustained pressure
+elevation in the caudal segment. In other words, the energy of the
+to-and-fro CSF movement is translated via the one-way valve into the
+creation and sustenance of syringomyelia.
 
@@
 Also, there is a possibility that some types of arachnoid pathology
-function as one-way valves. In 2014, we reported a case of thoracic
+function as one-way valves. In 2014, we reported cases of thoracic
 arachnoid web associated with syringomyelia, in which phase-contrast MRI
 detected one-way-valve-like behavior of the arachnoid web
-\cite{chang2014dorsal}. We found an obliquely oriented arachnoid web that
-reminded us of a one-way valve in surgery. Thus, our hypothesis may also
-solve the second theoretical problem that we pointed out in the
+\cite{chang2014dorsal}. In surgery, we found an obliquely oriented
+arachnoid web that reminded us of a one-way valve. Thus, our hypothesis may
+also solve the second theoretical problem we pointed out in the
 Introduction. Namely, we may consider the presence of a one-way valve in
 spinal subarachnoid space as a common mechanism underlying both
-Chiari-I-related and arachnopathy-related syringomyelia.  Our theory
-assumes that the arterial-pulse generated to-and-fro CSF movement provides
-the energy for syrinx generation. It is compatible with Stoodley et al.'s
+Chiari-I-related and arachnopathy-related syringomyelia.
+
+Our theory clearly explained how the energy of the to-and-fro CSF movement
+was transformed to CSF movement into the syrinx. However, previous
+theories seemed to have difficulty in explaining this process. According to
+the theories of Heiss et al. \cite{heiss1999elucidating} or that of
+Stoodley et al. \cite{stoodley2000mechanisms}, the energy is provided by
+either enhanced pressure waves in subarachnoid space or pulsation of spinal
+arteries. However, none of these theories explains the detailed mechanism
+
+hypothesized that arterial pulses drive CSF
+into the perivascular space of the cord matrix. Although his hypothesis
+explains the energy for syrinx generation, it fails to explain why
+manipulation of Our theory reasonably
+explained how the motion energy of the flowing CSF pumps CSF in the channel
+inside the spinal cord. It is compatible with Stoodley et al.'s
 experimental result that syrinx maintenance is dependent on arterial
-pulsation \cite{stoodley2000mechanisms}. In this study, the authors showed that
+pulsation . In this study, the authors showed that
+
+Our restuls may cast some light on another interesting question. In
+cervical spondylosis, subarachnoid space is similarly obliterated by the
+protruding discs and osteophytes. Although this is a widely prevaent
+disease, we rarely encounter syringomyelia associated with cervical
+spondylosis. In our results, a simple block of the subarachnoid CSF flow
+did not produce sustained elevation of intraspinal channel pressure (Video
+\cite{video:simple_block}.  This result may explain why syringomyelia is
+rarely associated with cervical spondylosis.
+
+There are some controversial points in our theory. Our model presumed the
+existence of a CSF channel inside the spinal cord. It may be controversial
+because most syringes seem to lack such communication. Yet, there still may
+exist a narrow CSF channel that is undetectable on MRI. In fact, ordinary
+MRI does not visualize the central canal with a diameter of 100
+micrometers. Therefore, assuming the existence of a CSF channel inside the
+cord will not be far-fetched. Another point of controversy will be the role
+of the central canal. The human central canal is obstructed with advancing
+age, and assuming a function of the central canal may not befit that fact.
+However, the obliteration of the central canal seem to be a slow process,
+and it could be mostly patent up to the fourth decade
+\cite{newman1981observations, yasui1999agerelated}. Moreover, the CSF
+channel does not have to be the central canal but some other channel
+created inside the spinal cord matrix.
 

### 2022-07-23 manuscript/main.tex
minor change

@@
 Video \ref{video:norm} shows the original system's response representing
-the normal condition. In this state, CSF made a smooth to-and-fro movement
+the normal condition. In this state, the dural tension made a smooth
+gradient along the spine, whose polarity alternated along the pressure
+cycle. According to this pressure gradient, CSF made a smooth to-and-fro movement
 in the subarachnoid space with the corresponding pressure wave along the

### 2022-08-01 manuscript/main.tex
rendering videos and some revision of the manuscript

@@
 \usepackage[T1]{fontenc}
+\usepackage{url}
 \usepackage{newfloat}
@@
 
-    The pathophysiology of syringomyelia is not well understood. The main
-    theoretical problem unaddressed by previous hypotheses is how
-    cerebrospinal fluid (CSF) enters from low-pressure subarachnoid space
-    to high-pressure syrinx and remains inside. We approached this problem
-    with a computer simulation of the CSF flow in the spine. We
-    hypothesized that to-and-fro movement of CSF across a
-    direction-selective resistance, via the pressure drop caused by the
-    resistance, pumps the CSF in the intraspinal channel distally.
+    The pathophysiology of syringomyelia is not well understood. Current
+    theories cannot explain a common mechanism for different types of
+    syringomyelia. Especially, they cannot explain how cerebrospinal fluid
+    (CSF) enters from low-pressure subarachnoid space to high-pressure
+    syrinx and remains inside. We approached this problem with a computer
+    simulation of the CSF flow in the spine. We hypothesized as follows.
+    Suppose there is a direction-selective CSF resistance at some point in
+    the subarachnoid space. A to-and-fro CSF movement across it will
+    produce an alternating asymmetric pressure gradient inside the spinal
+    cord, which subsequently drives the CSF in the intraspinal channel in
+    the resisted direction.
 
-    We constructed a model of CSF dynamics in the spine, which was an
-    electric circuit based on a lumped parameter model with multiple
-    compartments. The model assumed a CSF channel inside the spinal cord.
-    With this model, we could analyze the to-and-fro CSF movement of the
-    spine. We then created a direction-selective resistance in the
-    subarachnoid space. We changed a subarachnoid resistor so that it would
-    resist only to the caudally-directed flow.
+    We constructed a model of CSF dynamics in the spine, an electric
+    circuit based on a lumped parameter model with multiple compartments.
+    We then placed a direction-selective resistance in the subarachnoid
+    space so that it would resist only the caudal flow. We analyzed the
+    model's response to the to-and-fro CSF movement.
 
-    In the caudal flow phase, flow across the replaced resistor produced a
-    pressure drop in the distal subarachnoid segment. It subsequently
-    decreased the spinal-channel pressure in the distal segment; thus, the
-    pressure gradient across the point increased. This increased pressure
-    gradient pumped the CSF in the channel caudally. Because this
-    phenomenon did not occur in the rostral flow phase, the rostral flow in
-    the channel during this phase was smaller.  Overall, each cycle of
-    to-and-fro CSF movement pumped some CSF caudally in the spinal channel.
+    The to-and-fro CSF movement across the resistance produced a sustained
+    pressure elevation in the caudal intraspinal channel. This phenomenon
+    did not occur if the inserted resistance was bidirectional. The
+    detailed mechanism was as follows. Caudal flow across the
+    direction-selective resistor produced a pressure drop in the caudal
+    subarachnoid segment, subsequently decreasing the spinal-channel
+    pressure there. The resulting pressure gradient in the spinal channel
+    drove CSF caudally. Because this phenomenon did not occur in the
+    rostral flow phase, the rostral flow in the channel during this phase
+    was smaller. Overall, each cycle of to-and-fro CSF movement pumped some
+    CSF caudally in the spinal channel.
 
-    We could reasonably hypothesize that to-and-fro CSF movement across a
-    direction-selective resistance was the generative mechanism of
-    syringomyelia.
+    Our hypothesis provides a common mechanism for different types of
+    syringomyelia and explains how CSF is driven to the syrinx against the
+    pressure gradient.
 
@@
 \cite{serwayr.a.2016fluids, heiss1999elucidating, davis1989mechanisms,
-ellertsson1970distending}, which is understandable considering the elastic
-tension of the syrinx wall that the inside pressure confront. Therefore,
-merely assuming a communicating channel does not explain how CSF enters the
-syrinx against this pressure gradient and remains inside. Even if we take a
-specific time window where the subarachnoid pressure exceeds the syrinx
-pressure, it does not explain how the CSF remains inside the syrinx after
-it.
+ellertsson1970distending}; the inside pressure must additionally confront
+the elastic tension of the syrinx wall. Therefore, merely assuming a
+communicating channel does not explain how CSF enters the syrinx against
+this pressure gradient and remains inside. Even if we take a specific time
+window where the subarachnoid pressure exceeds the syrinx pressure, it does
+not explain how the CSF remains inside the syrinx after it.
 
@@
 CSF in an intraspinal channel caudally, causing syringomyelia. This
-hypothesis could solve the two problems discussed above. It could solve the
-paradox of CSF movement against the pressure gradient. Also, it could
-explain the pathophysiology of both Chiari-I-malformation-related
-syringomyelia and arachnopathy-related syringomyelia. The herniated
-cerebellar tonsils function as the selective resistance in Chiari-I
-malformation. And some arachnoid valve plays that role in
-arachnopathy-related syringomyelia \cite{chang2014dorsal}. However, in that
+hypothesis seemed to solve the two problems listed above.  However, in that
 article, we just drew a rough sketch of this process and left out a
@@
 
-Some problem exists in the computer simulation of the motion of biological
-fluids such as blood and CSF. Such bodily fluids move inside flexible
-tubes. It differs from the usual situation of fluid mechanics, where the
-boundary of the fluid conduit is solid. Thus, we cannot simply apply the
-standard Navier-Stokes equations for our simulation. For this reason,
-researchers have commonly used lumped parameter models \cite{shi2011review,
+There is a problem when we try to simulate the motion of biological fluids
+such as blood and CSF. Such bodily fluids move inside flexible tubes. It
+differs from the usual situation of fluid mechanics, where the boundary of
+the fluid conduit is solid. Thus, we cannot simply apply the standard
+Navier-Stokes equations for our simulation. For this reason, researchers
+have commonly used lumped parameter models \cite{shi2011review,
 kokalari2013review}. This model considers the fluid flow inside a flexible
@@
 version of the model used in our previous articles
-\cite{chang2003hypothesis, chang2004theoretical}. In this study, we did not
-intend to make a quantitatively precise model of the spinal CSF flow but to
-make a basic model that reveals the phenomenon underlying the generation of
+\cite{chang2003hypothesis, chang2004theoretical}.  We did not intend to
+make a quantitatively precise model of the spinal CSF flow but to make a
+basic model that could reveal the phenomenon underlying the generation of
 syringomyelia.
@@
 Previously, we developed a mathematical model that simulated the CSF flow
-in the spine \cite{chang2003hypothesis, chang2004theoretical}. This model (a
-multiple-compartment version of a 1-dimensional lumped parameter model)
+in the spine \cite{chang2003hypothesis, chang2004theoretical}. This model
+(a multiple-compartment version of a 1-dimensional lumped parameter model)
 could describe the CSF movement in the whole spine (Figure
-\ref{fig:model}). In this model, the \textit{D} capacitors represented the
-dural tension, \textit{C} capacitors the tension of the central canal,
-\textit{R} resistors the frictional resistance in the subarachnoid space,
-and \textit{r} resistors the frictional resistance in the central canal.
+\ref{fig:model}). This model assumed an intraspinal CSF channel---the
+central canal or some other equivalent channel.  In this model, the
+\textit{D} capacitors represented the dural tension, \textit{C} capacitors
+the tension of the central canal, \textit{R} resistors the frictional
+resistance in the subarachnoid space, and \textit{r} resistors the
+frictional resistance in the central canal.
 
@@
 calculate its behavior in response to a certain cranial pressure wave
-(defined as a boundary condition on the cranial nodes). This time, we
-improved the previous model as follows.
+(defined as a boundary condition on the cranial nodes). The concrete
+parameters were determined as follows.
 
@@
         thereby making the model more precise.
-    \item We revised the values of the parameters
-        (the capacitance and resistance of each component)
-        of the model as follows so that the model will become more realistic.
-        \begin{itemize}
-            \item First, we set the length of the modeled spinal cord to be 1 meter.
-            \item The resistance of the subarachnoid space ($R$) was
-                estimated using the following equations of Poisseuille
-                \cite{brook1999numerical, sherwin2003computational, huilgol2020fast}. 
+    \item We set the length of the modeled spinal cord to be 1 meter.
+    \item The resistance of the subarachnoid space ($R$) was estimated
+        using the following equations of Poisseuille
+        \cite{brook1999numerical, sherwin2003computational,
+        huilgol2020fast}.
+
              $$\Delta P=\frac{8\pi \mu{}LQ}{A^{2}}=RQ$$
+
         \begin{itemize}
@@
         \end{itemize}
-            \item Thus, $R$ was calculated to be $6872\hspace{0.2cm}(Pa\cdot{}sec/m^3)$
+    Thus, $R$ was calculated to be $6872\hspace{0.2cm}(Pa\cdot{}sec/m^3)$
     \item The resistance of the central canal ($r$) was estimated
@@
             Thus, $r$ was calculated to be $1.78\times10^{11}\hspace{0.2cm}(Pa\cdot{}sec/m^3)$
-        \end{itemize}
     \item We determined the capacitance ($C_{sub}$)corresponding to the dural elasticity so that the pressure-wave velocity determined by the time constant ($RC$) will roughly correspond to the pressure-wave velocity of the downward CSF wave observed in phase-contrast MRI of normal individuals.
@@
 model. This model represents the CSF movement in the spine as electric flow
-through multiple compartments of capacitances connected with resistors.
-Table 1 shows the values of the resistors and capacitors of the system. A
+through multiple compartments of capacitances connected with resistors. A
 set of differential equations can describe the behavior of this electric
@@
 set the step of the numerical solution to 1/5000 second and calculated the
-solution from zero to 20 seconds. We displayed the obtained solution as a
-movie in mp4 format.
+solution from zero to 20 seconds. The actual Mathematica codes can be found
+in our GitHub repository
+(\url{https://github.com/chang-hs/syrinx_simulation.git}).
 
@@
 
-We present the systems' responses in animations showing twenty cycles of
-to-and-fro waves. The x-axis of each animation represents the 100 nodes of
-the circuit laid out from the cranial to caudal direction. The y-axis
-displays some of the following four measures: the dural tension (voltage in
-D capacitors in Figure 2), the canal tension (voltages in C capacitors),
-the subarachnoid CSF flow (flows in R resistors), and the channel flow
-(flows in r resistors). We plotted the caudal flow in the positive and the
-rostral flow in the negative direction. The pressure values are shown in
-$cmH_2O$, the flows in $ml/sec$. To plot the four measures in a single
-animation, we multiplied the following three measures---the canal tension,
-the subarachnoid CSF flow, and the canal flow---with the following
+We present the systems' responses to twenty cycles of to-and-fro waves in
+animations. The x-axis of each animation represents the 100 nodes of the
+circuit laid out from the cranial to caudal direction. The y-axis displays
+some of the following four measures: the dural tension (voltage in D
+capacitors in Figure 2), the canal tension (voltages in C capacitors), the
+subarachnoid CSF flow (flows in R resistors), and the channel flow (flows
+in r resistors). We plotted the caudal flow in the positive and the rostral
+flow in the negative direction. The pressure values are shown in $cmH_2O$,
+the flows in $ml/sec$. To plot the four measures in a single animation, we
+multiplied the following three measures---the canal tension, the
+subarachnoid CSF flow, and the canal flow---with the following
 coefficients, respectively: namely, the canal tension with 50, the
@@
 
-Video \ref{video:norm} shows the original system's response representing
-the normal condition. In this state, the dural tension made a smooth
-gradient along the spine, whose polarity alternated along the pressure
-cycle. According to this pressure gradient, CSF made a smooth to-and-fro movement
-in the subarachnoid space with the corresponding pressure wave along the
-dura and the central canal. CSF also made smooth to-and-fro movements in
-the channel.
+Video 1 shows the original system's response representing the normal
+condition. In this state, the dural tension made a smooth gradient along
+the spine, whose polarity alternated along the pressure cycle. According to
+this pressure gradient, CSF made a smooth to-and-fro movement in the
+subarachnoid space with the corresponding pressure wave along the dura and
+the central canal. CSF also made smooth to-and-fro movements in the
+channel. There was almost no pressure elevation in the intra-spinal
+channel.
 
@@
 
-In Video \ref{video:simple_block}, we increased the subarachnoid resistance
+In Video 2, we increased the subarachnoid resistance
 $R_{25}$ by 20 times, thereby simulating a simple block of the subarachnoid
@@
 
-In Video \ref{video:oneway}, we replaced the subarachnoid resistor $R_{25}$
+In Video 3, we replaced the subarachnoid resistor $R_{25}$
 with a direction-selective resistor whose resistance to the rostral flow
 was unchanged but that to the caudal flow was increased by 20 times. This
-time, as shown in Video \ref{video:oneway}, sustained high pressure
-appeared in the central canal in the segment distal to the replaced
+time, sustained high pressure
+appeared in the intra-spinal channel in the segment distal to the replaced
 resistor, and sustained low pressure in the segment proximal to it. This
@@
 
-We took out the canal flow and showed it in Video 4. Observing this video,
-we can see that the cumulative total of the caudal flow is larger than that
-of the rostral flow, and it means that the CSF is virtually pumped caudally
-at node 25. To further elucidate this point, we plotted the canal flow in
-the simple block as shown in Video \ref{video:simple_block} and that in the
-one-way block as shown in Video \ref{video:oneway}. We can clearly see in
-this video that the caudal flow in the canal is
+We extracted the canal flow from this animation and showed it in Video 4.
+Observing this video, we can see that the cumulative total of the caudal
+flow is larger than that of the rostral flow, meaning that the CSF is
+virtually pumped caudally at node 25. To further elucidate this point,
+Video 4 simultaneously shows the canal flow in the simple block as shown in
+Video \ref{video:simple_block} and that in the one-way block as shown in
+Video \ref{video:oneway}. We can clearly see that the caudal flow is about
+the same in the two models, while the rostral flow is smaller in the
+direction-selective model. It means that CSF in the intra-spinal channel is
+pumped caudally in each cycle of the to-and-fro CSF movement.
 
@@
 In this article, we theoretically analyzed the CSF movement in the spine
-using a lumped parameter model with multiple components. It simulated a
+using a lumped parameter model with multiple compartments. It simulated a
 system with an elastic tube (dura) containing an elastic cylindrical
-material (spinal cord) that itself had a fluid channel inside (e.g. the
-central canal). When we placed a direction-selective resistor in the
-subarachnoid space and evoked a to-and-fro pressure wave on this system, it
-produced a sustained pressure elevation in the segment distal to the
-resistor in the resisted direction. This phenomenon may explain the
-pathogenesis of syringomyelia both in Chiari I malformation and
-syringomyelia associated with arachnopathy.
+material (spinal cord) that itself had a fluid channel inside.  When we
+placed a direction-selective resistor in the subarachnoid space and evoked
+a to-and-fro pressure wave on this system, it produced a sustained pressure
+elevation in the segment distal to the resistor in the resisted direction.
+This phenomenon may explain the pathogenesis of syringomyelia both in
+Chiari I malformation and syringomyelia associated with arachnopathy.
 
 Subarachnoid pressure pushes the spinal cord material and affects the
-pressure inside the central canal. As seen in Figure \ref{fig:circuit}, the
-absolute pressure inside the central canal is the sum of the subarachnoid
-and canal tension (voltages of $C_k$ and $D_k$ in electrical terms).
-Suppose a one-way valve selectively resists caudal flow in the subarachnoid
-space at point $A$. Caudal CSF flow creates a pressure drop across point
-$A$, with the caudal pressure smaller than the proximal one. Thus, the
-absolute pressure in the canal distal to point $A$ become smaller because
-the outside subarachnoid pressure there is smaller. It, therefore, creates
-a pressure gradient in the central canal across point $A$, thereby
-increasing the distal CSF flow in the canal at that point (Figure
-\ref{fig:pump_close}).
+pressure inside the intra-spinal channel. As seen in Figure
+\ref{fig:circuit}, the absolute pressure inside the intra-spinal channel is
+the sum of the subarachnoid and channel tension (voltages of $C_k$ and
+$D_k$ in electrical terms).  Suppose a one-way valve selectively resists
+caudal flow in the subarachnoid space at point $A$. Caudal CSF flow creates
+a pressure drop across point $A$, with the caudal pressure smaller than the
+proximal one. Thus, the absolute pressure in the canal distal to point $A$
+become smaller because the outside subarachnoid pressure there is smaller.
+It, therefore, creates a pressure gradient in the central canal across
+point $A$, thereby increasing the distal CSF flow in the canal at that
+point (Figure \ref{fig:pump_close}).
 
@@
 
-This theory successfully explains how CSF is pumped against the pressure
-gradient and remains inside the syrinx, one of the problems pointed out in
-the Introduction. A one-way valve in subarachnoid space creates an
-asymmetry of the pressure gradient between the caudal and rostral flow
-phases in the central canal. This asymmetric alternation of pressure
-gradient effectively pumps CSF caudally, creating sustained pressure
-elevation in the caudal segment. In other words, the energy of the
-to-and-fro CSF movement is translated via the one-way valve into the
-creation and sustenance of syringomyelia.
+Our theory clearly explained how the CSF is paradoxically driven into the
+high-pressure syrinx and retained inside against the pressure gradient.  In
+the direction-selective resistance model, the caudal segment of the
+intra-spinal channel has sustained higher pressure than the subarachnoid
+space. However, the energy of to-and-fro CSF movement creates alternating
+pressure gradient in the rostro-caudal direction. Because this
+rostro-caudal pressure gradient is larger than the sustained high pressure
+of the intra-spinal channel, CSF flows into the caudal segment from the
+rostral side during the caudal flow phase (Figure \cite{fig:pump_close}).
+In the rostral flow phase, the rostro-caudal pressure gradient is reversed
+in direction; the pressure on the rostral side becomes smaller than that on
+the caudal side. CSF flows out rostrally from the caudal intra-spinal
+channel; however, because the pressure-drop effect caused by the
+subarachnoid resistance is absent in this phase, the rostro-caudal pressure
+gradient in the intra-spinal channel is smaller and the rostral CSF flow is
+smaller than that during the caudal flow phase (Figure
+\cite{fig:pump_open}). We believe that this is the mechanism of the
+apparently paradoxical behavior of the CSF in syringomyelia.
 
-Direction-selective resistance to CSF flow is not an imaginative assumption
-but actually exists in patients. In Chiari-I malformation, the herniated
-tonsils move like a ball-valve, displaced caudally during the caudal flow
-and rostrally during the rostral flow. Higher velocity observed in the
-phase-contrast MRI studies suggests that it selectively impedes the caudal
-CSF flow more than the cranial flow. This direction-selective resistance
-was demonstrated by Williams in direct measurements in Chiari-I patients
-and became the basis of his theory \cite{williams1981simultaneous}.
+Direction-selective resistance to CSF flow is not an imaginative
+assumption. In Chiari-I malformation, the herniated tonsils move like a
+ball-valve; they are displaced caudally during the caudal flow and
+rostrally during the rostral flow. The higher velocity observed in the
+phase-contrast MRI studies suggests that they selectively impede the caudal
+CSF flow more than the cranial flow. Williams et al. demonstrated
+direction-selective resistance at the craniovertebral junction of Chiari-I
+patients, which became the basis of his theory
+\cite{williams1981simultaneous}.  Also, some types of arachnoid pathology
+may function as one-way valves. In 2014, we reported cases of thoracic
+arachnoid web associated with syringomyelia, in which phase-contrast MRI
+demonstrated one-way-valve-like behavior of the arachnoid web
+\cite{chang2014dorsal}. In surgery, we found an obliquely oriented
+arachnoid web that resembled a one-way valve. Thus, our hypothesis may also
+solve the second theoretical problem we pointed out in the Introduction.
+Namely, the direction-selective resistance in spinal subarachnoid space may
+function as the common mechanism underlying both Chiari-I-related and
+arachnopathy-related syringomyelia.
 
-Also, there is a possibility that some types of arachnoid pathology
-function as one-way valves. In 2014, we reported cases of thoracic
-arachnoid web associated with syringomyelia, in which phase-contrast MRI
-detected one-way-valve-like behavior of the arachnoid web
-\cite{chang2014dorsal}. In surgery, we found an obliquely oriented
-arachnoid web that reminded us of a one-way valve. Thus, our hypothesis may
-also solve the second theoretical problem we pointed out in the
-Introduction. Namely, we may consider the presence of a one-way valve in
-spinal subarachnoid space as a common mechanism underlying both
-Chiari-I-related and arachnopathy-related syringomyelia.
-
-Our theory clearly explained how the energy of the to-and-fro CSF movement
-was transformed to CSF movement into the syrinx. However, previous
-theories seemed to have difficulty in explaining this process. According to
-the theories of Heiss et al. \cite{heiss1999elucidating} or that of
-Stoodley et al. \cite{stoodley2000mechanisms}, the energy is provided by
-either enhanced pressure waves in subarachnoid space or pulsation of spinal
-arteries. However, none of these theories explains the detailed mechanism
-
-hypothesized that arterial pulses drive CSF
-into the perivascular space of the cord matrix. Although his hypothesis
-explains the energy for syrinx generation, it fails to explain why
-manipulation of Our theory reasonably
-explained how the motion energy of the flowing CSF pumps CSF in the channel
-inside the spinal cord. It is compatible with Stoodley et al.'s
-experimental result that syrinx maintenance is dependent on arterial
-pulsation . In this study, the authors showed that
+transformed into the energy-requiring trasport of CSF
+into the syrinx.  However, previous theories seemed to have difficulty in
+explaining this process.  According to the theories of Heiss et al.
+\cite{heiss1999elucidating} or that of Stoodley et al.
+\cite{stoodley2000mechanisms}, the energy is provided by either enhanced
+pressure waves in subarachnoid space or pulsation of spinal arteries.
+However, none of these theories explains the detailed mechanism
 
@@
 did not produce sustained elevation of intraspinal channel pressure (Video
-\cite{video:simple_block}.  This result may explain why syringomyelia is
+2).  This result may explain why syringomyelia is
 rarely associated with cervical spondylosis.
